---
title: "FrEDI Testing Markdown"
author: "CIRA Team"
output: 
  html_document:
    theme: lumen
params:
  ref:
    value: ref_temp
  comp:
    value: comp_branch
  inputs_ref:
    value: inputs_2300comp
  inputs_comp:
    value: inputs_2300Ref
---

<!-- Load Packages -->

```{r loadPackages, include=FALSE}
### Packages
require(tidyverse)
require(plotly)
require(glue)
require(ggpubr)
require(ggplot2)
require(lattice)
require(htmltools)
require(ggh4x)
require(kableExtra)
require(gridExtra)
```


<!-- Set Document Options -->

```{r docOpts, include=FALSE}
knitr::opts_chunk$set(message=FALSE)
```



<!-- Load Data -->

```{r loadData, include=FALSE}
dataDir   <- ".." |> file.path("data_tests")
fileExt   <- "."  |> paste0("rds")

strComp   <- "comp"
strRef    <- "ref"

fileComp  <- strComp  |> paste0("Results") |> paste0(fileExt)
fileRef   <- strRef   |> paste0("Results") |> paste0(fileExt)

pathComp  <- dataDir  |> file.path(fileComp)
pathRef   <- dataDir  |> file.path(fileRef)

comp_2300 <- pathComp |> readRDS()
ref_2300  <- pathRef  |> readRDS() 
```


<!-- Setup Common Plot Elements -->

```{r commonPlotElements, include=FALSE}
strRef      <- "ref"
strComp     <- "comp"
# argStrRef   <- "{params$ref}"
# argStrComp  <- "{params$comp}"
rc_str      <- strRef |> c(strComp)
rc_argStr   <- rc_str |> map(function(x){paste0("{params$", x, "}")}) |> set_names(rc_str)

yearStr     <- "year"
tempStr     <- "temp"
slrStr      <- "slr"
gdpStr      <- "gdp"
popStr      <- "pop"
gpcStr      <- "gdp_percap"
inputsStr   <- c(tempStr, slrStr, gdpStr, popStr, gpcStr)

frediLab    <- "FrEDI"
yearLab     <- "Year"
tempCLab    <- "Temperature (°C)"
conusLab    <- "CONUS"



listPlotTitles <- list()
rc_str
listPlotTitles[["rc_str"  ]] <- rc_str |> as.list() |> set_names(rc_str)
listPlotTitles[["argStr"  ]] <- rc_argStr

inputPlotArgs <- list() 
inputPlotArgs[["yCol"]] <- c("temp_C", "modelUnitValue", "gdp_usd", "pop", "gdp_percap") |> 
  map(function(title0, fredi0=frediLab){fredi0 |> paste(title0)}) |> set_names(inputsStr)
inputPlotArgs[["title"]] <- c("Temperatures", "Sea Level Rise (Calculated from Temperatures)", "U.S. GDP", "Population", "U.S. GDP per Capita") |> 
  map(function(title0, fredi0=frediLab){fredi0 |> paste(title0)}) |> set_names(inputsStr)
inputPlotArgs[["yLab"]] <- c(conusLab |> paste(tempCLab), "GMSL (cm)", "U.S. GDP (2015$ Trillions)", "Population (Millions)", "U.S. GDP per Capita (2015$ Thousands / capita)") |> 
  map(function(title0, fredi0=frediLab){fredi0 |> paste(title0)}) |> set_names(inputsStr)
inputPlotArgs[["k0"]] <- c(1, 1, 1e12, 1e6, 1e3) |> 
  map(function(title0, fredi0=frediLab){fredi0 |> paste(title0)}) |> set_names(inputsStr)

```


<!-- Setup Common Objects -->

```{r commonObjects, include=F}
paramInputsList <- list()
paramInputsList[["ref" ]] <- inputs_ref
paramInputsList[["comp"]] <- inputs_comp

resultsList <- list()
resultsList[["ref" ]] <- ref_2300 [["results"]]
resultsList[["comp"]] <- comp_2300[["results"]]

sectorsList <- resultsList |> map(function(df0, col0="sector"){df0 |> pull(all_of(col0)) |> pull() |> unique()}) |> set_names(rc_str)
```


<!-- Custom Functions -->

```{r functions, include=F}
###### getInputPlot ------------------------
getInputPlot <- function(
    name0   = "ref", 
    input0  = "temp", 
    list0   = paramInputsList, 
    names0  = rc_argStr, 
    yCols0  = inputPlotArgs[["yCol"]], 
    ks0     = inputPlotTitles[["k0"]], 
    titles0 = inputPlotTitles[["title"]], 
    yLabs0  = inputPlotTitles[["yLab"]], 
    xLab0   = yearLab
){
  ### Input type
  doSlr  <- "slr" %in% input0
  doPop  <- "pop" %in% input0
  type0  <- case_when(doSlr | doPop, input0, .default=input0 |> paste0("Input"))
  ### Plot labels
  yLab0  <- yLabs0 [[input0]]
  sub0   <- names0 [[name0]]
  gg0    <- titles0[[input0]]
  ### Data
  k0     <- ks0   [[input0]]
  yCol0  <- yCols0[[input0]]
  df0    <- list0 [[name0]][[type0]]
  df0    <- df0 |> mutate(yCol = df0 |> pull(all_of(yCol0)))
  df0    <- df0 |> mutate(yCol = yCol  /  k0)
  ### Summarize data if population
  if(doPop) {df0 <- df0 |> group_by_at(c("region", "year")) |> summarize_at(c("pop"), sum, na.rm=T)} ### End if(doPop)
  ### Plot
  p0     <- df0 |> ggplot()
  if(doPop) {p0 <- p0 + geom_line(aes(x=year, y=yCol, color=region)) + scale_color_discrete("Region")}
  else      {p0 <- p0 + geom_line(aes(x=year, y=yCol))}
  p0     <- p0 + scale_x_continuous(xLab0)
  p0     <- p0 + scale_y_continuous(yLab0)
  p0     <- p0 + ggtitle(gg0 |> glue(), sub0)
  ### Return
  return(p0)
}

###### rbindListTibbles ------------------------
rbindListTibbles <- function(list0){
  ### Names
  repos0 <- list0 |> names()
  names0 <- list0 |> map(names) |> set_names(repos0)
  join0  <- names0[[2]] |> get_matches(y=names0[[1]])
  ### Bind data
  df0    <- list0 |> map(select, all_of(join0)) |> set_names(repos0) |> bind_rows(.id="repo")
  ### Return data
  return(df0)
}

###### selectCols ------------------------
### Select specific columns
selectCols <- function(
    df0,    ### E.g., outputs of rbindListTibbles
    cols0  = c("sector", "variant", "region", "model", "model_type", "year", "annual_impacts", "repo"),
    allOf0 = TRUE
){
  ### Select columns
  if(allOf0) df0 <- df0 |> select(all_of(selectCols))
  else       df0 <- df0 |> select(any_of(selectCols))
  ### Return
  return(df0)
}

###### getNationalAgg ------------------------
applyFilters <- function(
    df0,        ### E.g., outputs of rbindListTibbles
    national    = TRUE, ### Whether to filter to national
    modelaves   = TRUE, ### Whether to filter to model averages/interpolation
    aggSectors  = TRUE, ### Whether to filter to specific sectors for aggregation
    aggVariants = TRUE  ### Whether to filter to sector-specific primary variants
){
  ### Filter to national average
  ### Filter to model averages
  ### Filter to primary variants and sectors
  if(national   ) df0 <- df0 |> filter(region == "National Total")
  if(modelaves  ) df0 <- df0 |> filter(model %in% c("Average", "Interpolation"))
  if(aggSectors ) df0 <- df0 |> filter(includeaggregate == 1)
  if(aggVariants) df0 <- df0 |> filter(sectorprimary == 1)
  ### Return
  return(df0)
}

###### getNationalSum ------------------------
getNationalSum <- function(
  df0, ### E.g., outputs of rbindListTibbles
  sum0  = "annual_impacts"
){
  ### Filter to aggregated national values
  df0    <- df0 |> applyFilters(national=TRUE, modelaves=TRUE, aggSectors=TRUE, aggVariants=TRUE)
  # ### Add Columns indicating the column used for summarization and version
  df0    <- df0 |> mutate(sumCol = sum0 )
  ### Summarize by region and year
  group0 <- c("region", "year", "repo", "sumCol")
  df0    <- df0 |> group_by_at(c(group0)) |> summarize_at(c(sum0), sum, na.rm=T)
  ### Return
  return(df0)
}

###### calcPctDiffs ------------------------
calcPctDiffs <- function(
  # list0, ### E.g., outputs of getNationalAgg
  df0, ### E.g., outputs of getNationalSum
  sumCol0  = "sumCol",
  repoCol0 = "repo",
  sum0     = "annual_impacts"
){
  # ### Add long format to list
  # list0  <- list()
  # list0[["long"]] <- df0
  ### Get unique values
  sum0   <- df0   |> pull(all_of(sumCol0 )) |> unique() 
  repo0  <- df0   |> pull(all_of(repoCol0)) |> unique() 
  sums0  <- sum0  |> paste0("_", repo0)
  ### Add column name
  drop0  <- c(repoCol0)
  df0    <- df0 |> mutate(colName=df0 |> pull(all_of(sumCol0)) |> paste0("_", df0 |> pull(all_of(repoCol0))))
  df0    <- df0 |> select(-any_of(drop0))
  df0    <- df0 |> pivot_wider(all_of(sum0), names_from=colNames, values_from=all_of(sum0))
  ### Calculate differences
  col0   <- sum0 |> paste0("_", "pctDiff")
  vals1  <- df0  |> pull(sums0[1])
  vals2  <- df0  |> pull(sums0[2])
  df0[[col0]] <- case_when(val2 == val1 ~ 0, .default=(vals2 - vals1) / vals1 * 1e2)
  # list0[["wide"]] <- df0
  # rm(df0)
  ### Return
  gc(verbose=FALSE)
  return(df0)
  # return(list0)
}

###### plotPctDiffs ------------------------
plotPctDiffs <- function(
    df0,      ### Wide format in list output from calcPctDiffs()
    yCol0     = "annual_impacts_pctDiff",
    thresh0   = 0.5,
    title0    = "Percent Difference" |> paste("Between Two Versions of FrEDI"),
    subTitle0 = "All Impacts",
    xLab0     = yearLab,
    yLab0     = "Percent Difference",
    colors0   = list(colors=list(low="#ffe4bf", mid="#ed781f", high="#6e0208"))
){
  ### Calculate color threshold
  df0      <- df0 |> mutate(yCol     = df0 |> pull(all_of(yCol0)))
  df0      <- df0 |> mutate(yColAbs  = yCol |> abs())
  df0      <- df0 |> mutate(colorCol = yColAbs >= thresh0)
  ### Plot elements
  yLab0    <- title0 |> paste0(" (", subTitle0, ")")
  lgdLab   <- paste0("|", title0, "|") |> paste(">=", thresh0)
  # title0   <- title0
  title0   <- title0 |> glue()
  ### Create plot
  p0       <- df0 |> ggplot()
  p0       <- p0 + geom_line(aes(x=year, y=yCol, colour=colorCol), alpha=0.75)
  p0       <- p0 + scale_x_continuous(xLab0)
  p0       <- p0 + scale_y_continuous(yLab0)
  p0       <- p0 + scale_colour_gradient(lgdLab, low=colors0$colors$low, high=colors0$colors$high)
  # p0       <- p0 + scale_colour_gradient2(lgdLab, low=colors0$colors$low, mid=colors0$colors$mid, high=colors0$colors$high, midpoint=thresh0)
  p0       <- p0 + ggtitle(title0, subTitle0)
  ### Ggplotly
  p0       <- p0 |> ggplotly()
  ### Return
  gc(verbose=FALSE)
  return(p0)
}

###### plotTwoRuns ------------------------
plotTwoRuns <- function(
    df0,      ### Wide format in list output from calcPctDiffs()
    yCol0     = "annual_impacts",
    title0    = "Comparison" |> paste("Between Two Versions of FrEDI"),
    subTitle0 = "All Impacts",
    xLab0     = yearLab,
    yLab0     = "Annual Impacts (2015$ Billions)",
    colorLab0 = "Version (Repo)",
    k0        = 1e9
){
  ### Calculate color threshold
  df0      <- df0 |> mutate(yCol = df0 |> pull(all_of(yCol0)))
  df0      <- df0 |> mutate(yCol = yCol / k0)
  ### Plot elements
  title0   <- title0 |> glue()
  ### Create plot
  p0       <- df0 |> ggplot()
  p0       <- p0 + geom_line(aes(x=year, y=yCol, color=repo), alpha=0.75)
  p0       <- p0 + scale_x_continuous(xLab0)
  p0       <- p0 + scale_y_continuous(yLab0)
  p0       <- p0 + scale_colour_discrete(colorLab0)
  p0       <- p0 + ggtitle(title0)
  ### Ggplotly
  p0       <- p0 |> ggplotly()
  ### Return
  gc(verbose=FALSE)
  return(p0)
}
```



## FrEDI Analysis {.tabset .tabset-fade .tabset-pills}

<font size = "5">**Comparing Branches** < / font>

<font size = "3"> `r paste("Reference Branch Name: *", params$ref, "*", sep="")` < / font>

<font size = "3">`r paste("Comparison Branch Name: *", params$comp, "*", sep="")` < / font>

### Analysis {.tabset}

#### Input Plots {.tabset .tabset-fade .tabset-pills}

##### Temperature Inputs

```{r echo=FALSE, fig.height = 7, fig.width = 15}
tempPlotList <- rc_str |> map(getInputPlot, list0=paramInputsList, input0="temp") |> set_names(rc_str)
tempPlotList |> gridExtra::marrangeGrob(ncol=2)
rm(tempPlotList)
# grid.arrange(ref_temp, comp_temp, ncol=2)
```

##### SLR Inputs

```{r echo=FALSE, fig.height = 7, fig.width = 15}
slrPlotList <- rc_str |> map(getInputPlot, list0=paramInputsList, input0="slr") |> set_names(rc_str)
slrPlotList |> gridExtra::marrangeGrob(ncol=2)
rm(slrPlotList)
```

##### GDP Inputs

```{r echo=FALSE, fig.height = 7, fig.width = 15}
gdpPlotList <- rc_str |> map(getInputPlot, list0=paramInputsList, input0="gdp") |> set_names(rc_str)
gdpPlotList |> gridExtra::marrangeGrob(ncol=2)
rm(gdpPlotList)
```

##### Population Inputs

```{r echo=FALSE, fig.height = 7, fig.width = 15}
popPlotList <- rc_str |> map(getInputPlot, list0=paramInputsList, input0="pop") |> set_names(rc_str)
popPlotList |> gridExtra::marrangeGrob(ncol=2)
rm(popPlotList)
```


#### Comparison of All Impacts {.tabset .tabset-fade .tabset-pills}

This section plots values for all impacts combined. These impacts include values for:

* Sector-specific primary variants
* Sectors selected for aggregation

Note that the extreme temperature mortality sector impacts have not been adjusted to account for Suicides in these plots.

<!-- Prepare data, calculate percentage differences -->
```{r aggregateNational, include=FALSE, echo=FALSE}
df_results  <- resultsList |> rbindListTibbles(); df_results |> glimpse()
sum_results <- df_results  |> getNationalSum(sum0="annual_impacts"); sum_results |> glimpse()
sum_pctDiff <- sum_results |> calcPctDiffs  (sum0="annual_impacts"); sum_pctDiff |> glimpse()
# comp_2300_pct_diff_nat_2101 <- comp_2300$results |> filter(year %in% c(2100, 2101))
```

Plot comparing annual impacts for national totals (sum of model averages for primary sector variants and sectors selected for aggregation); 

```{r prepare_nat_2300_data, include=FALSE, echo=FALSE}
sum_results |> plotTwoRuns()
```

Plot of percentage difference between annual impacts for national totals (sum of model averages for primary sector variants and sectors selected for aggregation); 

```{r prepare_nat_2300_data, include=FALSE, echo=FALSE}
sum_pctDiff |> plotPctDiffs()
```





#### Sector Comparisons

```{r prepare_2300_data, include=FALSE, echo=FALSE}
sect_results <- df_results |> 
  applyFilters(national=TRUE, modelaves=TRUE, aggSectors=FALSE, aggVariants=FALSE) |>
  selectCols() |>
  mutate(sumCol = "annual_impacts")
sect_pctDiff <- sect_results |> calcPctDiffs()


# comp_2300_pct_diff <- comp_2300$results |>
#   #FrEDI::aggregate_impacts(aggLevels = c("all")) |>
#   rename("annual_impacts_comp" = annual_impacts) |>
#   filter(region == "National Total") |> 
#   filter(model %in% c("Average", "Interpolation")) |>
#   select(sector, variant, region, model, model_type, year, annual_impacts_comp) 
# 
# 
# sectors_comp <- comp_2300_pct_diff$sector 
# 
# ref_2300_pct_diff <- ref_2300$results |>
#   #FrEDI::aggregate_impacts(aggLevels = c("all")) |>
#   rename("annual_impacts_ref" = annual_impacts) |>
#   filter(region == "National Total") |> 
#   filter(model %in% c("Average", "Interpolation")) |>
#   select(sector, variant, region, model, model_type, year, annual_impacts_ref) 
# 
# compare_pct_diff <- left_join(ref_2300_pct_diff, comp_2300_pct_diff) |> 
#   mutate(ann_imp_perc_diff = ((annual_impacts_comp - annual_impacts_ref) / annual_impacts_ref) * 100
#   )
# # test <- ref_2300_pct_diff |> filter( sector == "ATS Temperature-Related Mortality")
# rm(comp_2300_pct_diff, ref_2300_pct_diff)
# 
# comp_2300_run <- comp_2300$results |>
#   #FrEDI::aggregate_impacts(aggLevels = c("all")) |>
#   mutate(run = "comp") |>
#   filter(region == "National Total") |> 
#   filter(model %in% c("Average", "Interpolation")) |>
#   filter(sectorprimary == 1) |>
#   select(run, sector, variant, region, model, model_type, year, annual_impacts) 
# sectors_run <- comp_2300_run$sector 
# 
# ref_2300_run <- ref_2300$results |>
#   #FrEDI::aggregate_impacts(aggLevels = c("all")) |>
#   mutate(run = "ref") |>
#   filter(region == "National Total") |> 
#   filter(model %in% c("Average", "Interpolation")) |>
#   filter(sectorprimary == 1) |>
#   select(run , sector, variant, region, model, model_type, year, annual_impacts) 
# 
# compare_2300run <- full_join(ref_2300_run, comp_2300_run)
# rm(comp_2300_run, ref_2300_run)
# gc(verbose =FALSE)

pct_diff_plots <- compare_pct_diff |> 
  filter(model %in% c("Average", "Interpolation")) |>
  group_by(sector) |>
  nest() %>%
  mutate(plot = map2(data, sector, 
                     ~ ggplotly(
                       ggplot(data = .x, aes(x = year, y = ann_imp_perc_diff, colour= (0.5 > ann_imp_perc_diff & ann_imp_perc_diff > -0.5))) +
                         geom_line() +
                         scale_colour_manual(name = ' 0.5> %_diff > -0.5', values = setNames(c('green', 'red'), c(T, F))) +
                         facet_grid2(.~ variant, scales="free") +
                         #theme_gray() +
                         ggtitle(glue("Percent Difference: {.y}"))
                     )
  )
  )

ref_comp_plots <- compare_2300run |> 
  filter(model %in% c("Average", "Interpolation")) |>
  group_by(sector) |>
  nest() %>%
  mutate(plot = map2(data, sector, 
                     ~ ggplotly(ggplot(data = .x, aes(x = year, y = annual_impacts, group = run)) +
                                  geom_line(aes(color=run)) +
                                  facet_wrap(~ variant, scales="free") +
                                  ggtitle(glue("ref vs comp FrEDI: {.y}"))
                     )
  )
  )

plots <- full_join(pct_diff_plots, ref_comp_plots)|> dplyr::arrange(sector)
rm(ref_comp_plots, pct_diff_plots)
gc(verbose =FALSE)
```

```{r plot2300_Data , echo=FALSE}
htmltools::tagList(plots$plot)
```

------------------------------------------------------------------------


