---
title: "Configure Main FrEDI Data"
author: "Industrial Economics, Inc."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_document:
    theme: spacelab
    toc: true
    toc_float: true
---

<style>
/* Simplified version of Bootstrap's responsive table CSS */
.table-responsive {
display: block;
width: 100%;
overflow-x: auto;
}

.table-responsive > table {
width: 100%;
}
</style>


```{r knitr setup, include=FALSE}
### The following parameters declare the options for compiling the Markdown document.
knitr::opts_chunk$set(
  include = T,     ### Evaluate and depict outputs of code chunks in the compiled document
  echo    = T,     ### Echo the commands of the code chunks in the compiled document
  message = FALSE, ### Don't include command-line messages output from evaluating code chunks
  cache   = FALSE, ### Don't cache the evaluation of code chunks
  warning = FALSE,  ### Don't include warnings from evaluating code chunks
  table.format = "html" 
)
```

## Overview

The purpose of this package is to configure the data for the main FrEDI tool. 

Load packages 

```{r loadPackages}
### Packages
require(tidyverse)
require(openxlsx)
require(devtools)
```


Date of most recent version of the Excel configuration file:

```{r mostRecentDate}
mostRecentDate <- "20230503"
```



```{r declare paths}
### Set print options
# options(digits = 20)
### Set system paths
# projectPath      <- getwd()
projectPath      <- "."
today            <- format(Sys.Date(), "%Y%m%d")

### Path to fredi project
projectParentDir <- projectPath %>% file.path("..")
projectParentDir %>% list.files
frediPath        <- projectParentDir %>% file.path("FrEDI")

### Project configuration
configPath       <- projectPath %>% file.path("config")
# configFiles      <- configPath %>% list.files(".R")
configFiles      <- "frediConfig.R"
### Code path
codePath         <- projectPath %>% file.path("R")
codeNames        <- codePath %>% list.files(".R")
configLogPath    <- codePath %>% file.path("configLog")

### Names for archive and use versions
configFileName   <- "fredi_config"
configArchName   <- configLogPath %>% file.path(configFileName) %>% paste(today, sep="_") %>% paste0(".rda")
configUseName    <- codePath %>% file.path(configFileName) %>% paste0(".rda")

### Output path
dataOutPath      <- projectPath %>% file.path("data")
dataOutLog       <- dataOutPath %>% file.path("dataLog")
sysFileName      <- "sysdata"
sysArchName      <- dataOutLog %>% file.path(sysFileName) %>% paste(today, sep="_") %>% paste0(".rda")
excelFileName    <- mostRecentDate %>% paste("FrEDI_config.xlsx", sep="_")
sysUseName       <- dataOutPath %>% file.path(sysFileName) %>% paste0(".rda")

### Name of most recent sysdata.rda file in archive
dataOutLogFiles  <- dataOutLog %>% list.files %>% sort(decreasing = T); dataOutLogFiles %>% head
sysFileRef       <- dataOutLog %>% file.path(dataOutLogFiles[1]); sysFileRef
# sysFileRef       <- dataOutLog %>% file.path("sysdata_20221021.rda"); sysFileRef
```

<!-- ### Configuration Files -->

Load all configuration functions

```{r load config}
### Load all functions
configFiles; for(i in configFiles){ source(paste(configPath, i, sep="/")) }
```


List configuration files

```{r}
configLogPath %>% list.files("rda") %>% sort(decreasing=FALSE) %>% head
```

Update archive:

```{r}
frediConfig(outPath = configArchName)
```

Confirm copy was saved:

```{r}
basename(configArchName) %in% (configLogPath %>% list.files("rda"))
```

## Create Tool Configuration Data

### 1. Load Data

Load data from Excel configuration file:

```{r list_loadData}
### Load all functions
# codeNames; 
for(i in codeNames){ source(paste(codePath, i, sep="/")) }
### list_loadData
list_loadData <- loadData( 
  fileDir   = "." %>% file.path("..", "createSystemData","inst", "extdata"), ### Path to project
  fileName  = excelFileName, ### name of excel file with config information
  sheetName = "tableNames",
  silent = NULL
)
```

<!-- Check scaled impacts -->

<!-- ```{r} -->
<!-- test_impacts0  <- list_loadData$data_scaledImpacts -->
<!-- names_impacts0 <- test_impacts0 %>% names -->
<!-- check_impacts0 <- test_impacts0 %>% group_by_at(.vars=c(all_of(names_impacts0))) %>% summarize(n=n(), .groups="keep") %>% ungroup  -->
<!-- test_impacts0 %>% glimpse -->
<!-- check_impacts0 %>% glimpse -->
<!-- check_impacts0 %>% filter(n>1) %>% glimpse -->
<!-- ``` -->


### 2. Reshape Loaded Data

Reshape loaded Excel data

```{r list_reshapeData}
### Load all functions
# codeNames; 
for(i in codeNames){ source(paste(codePath, i, sep="/")) }
### list_reshapeData
list_reshapeData <- list_loadData %>% reshapeData(silent=T)
```

<!-- Check scaled impacts -->

<!-- ```{r} -->
<!-- test_impacts0  <- list_reshapeData$data_scaledImpacts -->
<!-- names_impacts0 <- test_impacts0 %>% names -->
<!-- check_impacts0 <- test_impacts0 %>% group_by_at(.vars=c(all_of(names_impacts0))) %>% summarize(n=n(), .groups="keep") %>% ungroup  -->
<!-- test_impacts0 %>% glimpse -->
<!-- check_impacts0 %>% glimpse -->
<!-- check_impacts0 %>% filter(n>1) %>% glimpse -->
<!-- ``` -->


### 3. Configure Data

Test `createSystemData()` function (configure reshaped data)

```{r list_systemData0}
for(i in codeNames){ source(paste(codePath, i, sep="/")) }
# frediPath %>% load_all
### Uncomment following two lines to create and save data and check the outputs
time1            <- Sys.time()
list_systemData0 <- list_reshapeData %>% createSystemData(save=F, silent=T)
time2            <- Sys.time()
time_create      <- time2 - time1; time_create
```


### 4. Tests 

#### Parameters

Parameters for saving tests

```{r test parameters}
save_test   <- TRUE
return_test <- TRUE
```


#### Reshaped Data Test

<!-- Try different methods -->

<!-- ```{r} -->
<!-- test_types <- c("data.frame", "tibble") -->
<!-- test_list  <- list(a=test_types, b=c("list")) -->
<!-- test_list1 <- test_list %>% names %>% map(~case_when(("data.frame" %in% test_list[[.]])~1, ("list" %in% test_list[[.]])~2, TRUE~0)) -->
<!-- test_list2 <- test_list %>% names %>% map(~case_when(("data.frame" %in% test_list[[.]])~"data.frame", ("list" %in% test_list[[.]])~"list", TRUE~"N/A")) -->
<!-- test_list2 %>% length %>% seq_len %>% map(~(test_list2[[.]] %>% print)) -->
<!-- test_list2 %>% length %>% seq_len %>% map(~(if_else("data.frame" %in% test_list2[[.]], 1, 0))) -->
<!-- ``` -->


Try the test for the reshaped data:

```{r test_reshapeData}
for(i in codeNames){ source(paste(codePath, i, sep="/")) }
test_reshapeData   <- list_reshapeData %>% dataInfo_test(
  csvName = "reshapedData_testResults",
  save    = save_test,
  return  = return_test
)
```

Examine reshaped data test results: check for any tables that didn't pass


```{r}
test_reshapeData %>% filter(passed!=1)
```




#### General Config Tests

Try the general tests for configured data:

```{r test_systemData0}
for(i in codeNames){ source(paste(codePath, i, sep="/")) }
test_systemData0 <- list_systemData0 %>% dataInfo_test(
  csvName = "configuredData_testResults",
  save    = save_test,
  return  = return_test
)
```


Examine configured data test results: check for any tables that didn't pass



```{r}
test_systemData0 %>% filter(passed!=1)
```



#### General Tests

Wrap the general tests into a single wrapper function:

```{r test general_config_test}
for(i in codeNames){ source(paste(codePath, i, sep="/")) }
test_general_config <- general_config_test(
  reshapedData   = list_reshapeData,
  configuredData = list_systemData0,
  overwrite      = TRUE,
  fredi_config = fredi_config
)
```


#### New Sector Tests

Run `createSystemData()` tests:

(remove objects )
```{r test configTest_newSectors}
for(i in codeNames){ source(paste(codePath, i, sep="/")) }
test_newSectors_config <- newSectors_config_test(
  newData     = list_systemData0,
  refDataFile = sysFileRef,
  save      = save_test,
  return    = return_test
)
```


#### Check FrEDI

Compare FrEDI outputs with recent changes to past FrEDI outputs.

```{r test FrEDI defaults}
### Load FrEDI code and get default results
frediPath %>% load_all
def_fredi0  <- run_fredi()
```

Compare the results

```{r test_fredi0}
### Load test code
for(i in codeNames){ source(paste(codePath, i, sep="/")) }
### Test results
test_fredi0 <- def_fredi0 %>% general_fredi_test(
  outPath   = ".",
  save      = save_test,
  return    = return_test,
  overwrite = TRUE
)
```


Examine FrEDI default results: check for any tables that didn't pass

```{r}
test_fredi0[["dataInfo_test"]] %>% filter(passed!=1)
test_fredi0[["outputs_diffs"]] %>% glimpse
```


## Update Data


If above passed tests, overwrite previous config

```{r save and overwrite data}
# codeNames; for(i in codeNames){ source(paste(codePath, i, sep="/")) }
### Uncomment following two lines to create and save data and check the outputs
time1           <- Sys.time()
list_systemData <- list_reshapeData %>% createSystemData(save=T, silent=T)
#list_systemData <- list_reshapeData %>% createSystemData(save=T, silent=T)
time2           <- Sys.time()
time_create     <- time2 - time1; time_create
```


**Manually update the sysdata.rda file in the Rtool.**

After copying and pasting the system data to the Rtool, try detaching the package and then loading the package functions. 

```{r file.copy}
file.copy(
  from = dataOutPath %>% file.path(sysFileName) %>% paste0(".rda"),
  to   = frediPath   %>% file.path("R", sysFileName) %>% paste0(".rda"),
  overwrite = T
)
```


## Test R Tool

Change the following code if there are new sectors

```{r new_sectors}
# c_sectorsList <- FrEDI::get_sectorInfo()
#c_sectorsList <- c("ATS Extreme Temperature", "Rail", "Coastal Properties","Vibrio")
c_sectorsList <- c("Vibrio", "Mental Health")

```


Test inputs

```{r testInputs}
### Values above maximum values
testInputs <- list(
  ramp = list(
    tempInput = data.frame( year = 2000:2300, temp_C = seq(-1, 20, length.out=301)),
    slrInput  = data.frame( year = 2000:2300, slr_cm = seq(0, 270, length.out=301))
  )
)
```





Try running the function

```{r test FrEDI function, message=T}
### Results are fine for ATS Extreme Temperature and Coastal Properties
frediPath %>% load_all
# test1 <- testInputs$max %>% run_fredi(sectorList = c_sectorsList, aggLevels="all")
# test1 <- testInputs$ramp %>% run_fredi(sectorList = c_sectorsList, aggLevels="none")
# test1 <- testInputs$ramp %>% run_fredi(sectorList = c_sectorsList, aggLevels="none", thru2300=T)
time3 <- Sys.time()
test1 <- testInputs$ramp %>% run_fredi(sectorList = c_sectorsList, aggLevels="all", maxYear=2100)
# test1 <- testInputs$ramp %>% run_fredi(sectorList = c_sectorsList, aggLevels="none", maxYear=2300)
time4 <- Sys.time(); time4 - time3
# test1 <- test1 %>% mutate(driverValue2 = driverValue %>% round(0))
test1 %>% glimpse
# test1 <- test1 %>% aggregate_impacts(aggLevels = "all")
test1$driverUnit %>% unique
```



<!-- ```{r} -->
<!-- c_sectorsList <- c("Vibrio") -->
<!-- gcm_temps <- openxlsx::read.xlsx("../CONUS Temperature Change.xlsx") |> -->
<!--  filter(Year >= 2000) -->
<!-- gcm_names <- names(gcm_temps)[2:7] -->


<!-- gcm_outputs <-map_df( -->
<!--  gcm_names, -->
<!--  function(x){ -->
<!--  print(x) -->
<!--  testInputs <- list( -->
<!--  ramp = list( -->
<!--  tempInput = data.frame(year = gcm_temps$Year, temp_C = gcm_temps[x] |> unname()), -->
<!--  slrInput = data.frame(year = gcm_temps$Year, slr_cm = seq(0, 270, length.out=length(gcm_temps$Year))) -->
<!--  )) -->
<!--  testInputs$ramp %>% run_fredi(sectorList = c_sectorsList, aggLevels=c("national", "modelaverage"), maxYear=2099) |> mutate(gcm_run_name = x) -->
<!--  } -->
<!-- ) -->

<!-- write_csv(gcm_outputs,"vibrio_gcm_runs.csv") -->

<!-- ``` -->




<!-- ## Check Configuration Data -->


<!-- Use the following code chunks to view/check outputs for the new sector (all data stored in a list called `list_systemData`) -->

<!-- ### Scalars -->


<!-- ```{r test_scalars} -->
<!-- list_systemData0$slrImpacts$scaled_impacts %>% range(na.rm=T) -->
<!-- ### test_scalars: dataframe with configuration values for scalars  -->
<!-- test_scalars <- list_systemData0$scalarDataframe -->
<!-- test_scalars %>% glimpse -->
<!-- ### test_mainScalars: dataframe with annual values for scalars  -->
<!-- test_mainScalars <- list_systemData0$df_mainScalars -->
<!-- test_mainScalars$scalarType %>% unique -->
<!-- (test_mainScalars %>% filter(scalarType=="econScalar"))$scalarName %>% unique -->
<!-- test_mainScalars %>% glimpse -->
<!-- # test_mainScalars_sum <- test_mainScalars %>% group_by_at(.vars=c("")) -->
<!-- ### test_mainScalars: dataframe with info about scalars -->
<!-- test_scalarInfo <- list_systemData0$co_scalarInfo -->
<!-- test_scalarInfo %>% glimpse -->

<!-- ### test_sectorsInfo: dataframe with info about sectors and scalars -->
<!-- test_sectorsInfo <- list_systemData0$df_sectorsInfo -->
<!-- test_sectorsInfo %>% glimpse -->

<!-- test_sectorsInfo %>% filter(sector=="Rail") %>% glimpse -->
<!-- ### Initial results -->
<!-- list_systemData0$df_results0 %>% glimpse -->
<!-- ``` -->


<!-- Examine missing values -->

<!-- ```{r test1_na} -->
<!-- (test1 %>% filter(driverUnit=="cm"))$year %>% range -->
<!-- (test1 %>% filter(driverUnit=="cm"))$year %>% range -->
<!-- test1_na <- test1 %>% filter(is.na(annual_impacts)) -->
<!-- test1_na %>% glimpse -->
<!-- test1_na$sector %>% unique -->
<!-- test1_na_sum <- test1_na %>% mutate(n=1) %>%  -->
<!--   group_by_at(.vars=c("sector", "variant", "impactYear", "impactType", "region", "model", "driverValue2")) %>%  -->
<!--   summarize_at(.vars=c("n"), sum) %>% ungroup -->
<!-- test1_na_sum %>% glimpse -->
<!-- ``` -->



<!-- Try plotting -->

<!-- ```{r test1 gcm, fig.width=8, fig.height=5} -->
<!-- test1 %>%  -->
<!--   filter(driverUnit!="cm") %>%  -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x=year, y=annual_impacts, color=region, group=interaction(impactType, variant, impactYear, model, region)), alpha = 0.4) +  -->
<!--   facet_grid(sector~model) +  -->
<!--   theme(legend.position="bottom", axis.text.x = element_text(angle=90)) -->
<!-- ``` -->



<!-- SLR -->

<!-- Check missing values -->

<!-- ```{r slr_check} -->
<!-- slr_check <- test1 %>% filter(driverUnit=="cm") %>% filter(is.na(annual_impacts)) -->
<!-- slr_check %>% glimpse -->
<!-- ``` -->


<!-- Look at results -->

<!-- ```{r slr test plots, fig.width=8, fig.height=5} -->
<!-- test1 %>%  -->
<!--   filter(driverUnit=="cm") %>%  -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x=year, y=annual_impacts, color=region, group=interaction(impactType, variant, impactYear, model, region)), alpha = 0.4) +  -->
<!--   facet_grid(sector~region) +  -->
<!--   theme(legend.position="bottom", axis.text.x = element_text(angle=90)) -->
<!-- ``` -->



<!-- Test ramp function -->






<!-- ```{r test_slr0} -->
<!-- # test_Inputs -->
<!-- test_slr0 <- testInputs$ramp$slrInput; test_slr0 %>% glimpse -->
<!-- # test_slr1 <- list_systemData$slrExtremes; test_slr1 %>% glimpse -->
<!-- test_slr2 <- test_slr0 %>% left_join(test_slr1, by=c("year")) %>% arrange_at(.vars=c("sector", "variant", "impactType", "impactYear", "region", "year")); test_slr2 %>% glimpse -->
<!-- test_slr3 <- test_slr2 %>% mutate(impact = impacts_intercept + impacts_slope * driverValue_ref); test_slr3 %>% glimpse -->
<!-- ``` -->







<!-- Visual check of impacts -->

<!-- ```{r test_plots_imp, fig.width=6, fig.height=4} -->
<!-- test_plots_imp <- test_slr3 %>%  -->
<!--   mutate(impact = impacts_intercept + impacts_slope * (slr_cm - driverValue_ref)) %>%  -->
<!--   mutate(value = impact) %>% -->
<!--   filter(year %in% seq(2000, 2300, by=10)) %>% -->
<!--   (function(data_x, title = "SLR Impact Values"){ -->
<!--     sectors_x <- data_x$sector %>% unique -->
<!--     list_x    <- sectors_x %>% lapply(function(sector_i){ -->
<!--       # ySub   <- "SLR Impact Slopes" -->
<!--       ## Filter data -->
<!--       # data_i <- data_x -->
<!--       data_i <- data_x %>% filter(sector==sector_i) -->
<!--       data_i$value %>% range %>% print -->
<!--       # data_i <- data_i %>% mutate(variant=variant %>% as.character) -->
<!--       # var_i  <- data_i$variant %>% unique; var_i %>% print -->
<!--       ### Get breaks -->
<!--       list_i <- data_i$value %>% get_plotBreaks -->
<!--       list_i %>% print -->
<!--       # list_i[c("breaks", "labels")] %>% lapply(function(y){length(y)}) %>% unlist %>% print -->
<!--       ### Adjust data -->
<!--       rnd_i  <- list_i$div %>% log10 %>% abs -->
<!--       # data_i <- data_i %>% mutate(value=value/list_i$div) -->
<!--       # data_i <- data_i %>% mutate(value=value %>% round(rnd_i)) -->
<!--       #### Plot data -->
<!--       plot_i <- data_i %>% ggplot() + geom_line(aes(x=year, y=value, group=interaction(impactType, variant, region), color = region, linetype=impactType), alpha = 0.4) + -->
<!--         facet_grid(.~region) -->
<!--       plot_i <- plot_i + theme(legend.position = "bottom") + theme(axis.text.x = element_text(angle=90)) -->
<!--       plot_i <- plot_i + ggtitle(title) -->
<!--       # plot_i <- plot_i + scale_y_continuous(list_i$yLab, limits=list_i$limits, breaks = list_i$breaks, labels=list_i$labels) -->
<!--       return(plot_i) -->
<!--     }) -->
<!--     names(list_x) <- sectors_x -->
<!--     return(list_x) -->
<!--   }) -->
<!-- test_plots_imp -->
<!-- ``` -->




<!-- ```{r test2} -->
<!-- frediPath %>% load_all -->
<!-- test2 <- testInputs$ramp %>% run_fredi(aggLevels="none") -->
<!-- ``` -->




<!-- Try the package: 167,184 rows -->

<!-- ```{r df_defaults, message=T} -->
<!-- frediPath %>% load_all -->
<!-- df_defaults <- run_fredi(sectorList = NULL, aggLevels=c("national", "modelaverage", "impactyear")) %>% filter(year %in% seq(2010, 2300, by=5))  -->
<!-- # df_defaults <- run_fredi(sectorList = c_sectorsList, aggLevels=c("national", "modelaverage", "impactyear")) %>% filter(year %in% seq(2010, 2300, by=5))  -->
<!-- # df_defaults <- FrEDI::run_fredi(sectorList = c_sectorsList, aggLevels="none") %>% filter(year %in% seq(2010, 2090, by=5)) -->
<!-- df_defaults %>% filter(sector=="ATS Extreme Temperature") %>% filter(region=="National Total") %>% filter(year==2090) %>% filter(model=="Average") -->
<!-- df_defaults %>% dim -->
<!-- df_defaults %>% filter(!is.na(annual_impacts)) %>% nrow -->
<!-- (df_defaults %>% filter(!is.na(annual_impacts)))$annual_impacts %>% range -->
<!-- (df_defaults %>% filter(!is.na(annual_impacts)))$sector %>% unique -->
<!-- ``` -->



<!-- Examine rounding -->

<!-- ```{r} -->
<!-- # Extreme Temperature, No Adaptation, 2090 socioeconomics, Cold, Midwest, CanESM2, 2070 -->
<!-- # sprintf(x, fmt = '%#.3f')  -->
<!-- test_digits <- df_defaults %>% -->
<!--   filter(year == 2070, region == "Midwest", model == "CanESM2") %>% -->
<!--   filter(sector == "Extreme Temperature", variant == "No Adaptation") %>%  -->
<!--   filter(impactYear == "2090", impactType == "Cold") %>%  -->
<!--   select(annual_impacts) %>% as.vector; test_digits -->

<!-- # test_digits %>% format(digits = 6) -->
<!-- # test_digits %>% sprintf(fmt = '%#.6f')  -->
<!-- # c(NA) %>% sprintf(fmt = '%#.6f')  -->
<!-- ### -239115535.389834 -->
<!-- ``` -->


<!-- Use the following code to save the results: -->

<!-- * Name the output path and create it if it doesn't exist. -->
<!-- * Then save the outputs file. -->


<!-- ```{r saveOutputsPath} -->
<!-- saveOutputsPath <- frediPath %>% file.path("..", "analysis", "qc", today) -->
<!-- if(!dir.exists(saveOutputsPath)){saveOutputsPath %>% dir.create} -->
<!-- test1 %>% write.csv(file = file.path(saveOutputsPath, paste0(today, "_qc_outputs.csv")), row.names=F, na="") -->
<!-- ``` -->






<!-- Create plots -->



<!-- ```{r plot types, fig.height=10, fig.width=16} -->
<!-- ### Create only heatmaps -->
<!-- # frediPath %>% paste("R", sep="/") %>% load_all() -->
<!-- # defPlots <- df_defaults %>% get_plots(plotTypes="heatmaps") -->
<!-- defPlots <- df_defaults %>% get_plots(plotTypes="heatmaps") -->
<!-- defPlots$heatmaps$SLR -->
<!-- ``` -->


<!-- ### Check SLR Outputs -->

<!-- #### SLR Drivers  -->



<!-- SLR drivers should have no missing values past 2090 and only one row for each `year~model` combo: -->

<!-- ```{r test_slr_cm} -->
<!-- # fun_slrModel2Height <- utils::getFromNamespace("fun_slrModel2Height", "FrEDI") -->
<!-- test_slr_cm <- list_systemData0$slr_cm %>%  -->
<!--   mutate(model_fact = model_dot %>% fun_slrModel2Height(include="values", valType="factor",labelType="character")) -->
<!-- test_slr_cm %>% glimpse -->
<!-- test_slr_cm %>% filter(year > 2090) %>% filter(is.na(driverValue)) %>% nrow -->
<!-- test_slr_cm %>% mutate(n=1) %>% group_by_at(.vars=c("year", "model")) %>% summarize_at(.vars=c("n"), sum) %>% filter(n>1) %>% nrow -->
<!-- ``` -->

<!-- Visual check of drivers  -->

<!-- ```{r, fig.width=6, fig.height=4} -->
<!-- test_slr_cm %>% ggplot() + geom_line(aes(x=year, y=driverValue, color = model_fact)) -->
<!-- ``` -->

<!-- #### SLR Scaled Impacts -->

<!-- SLR scaled impacts should have no missing values past 2090 and only one row for each `year~sector~variant~impactType~impactYear~region~model` combo: -->


<!-- ```{r test_imp_cm} -->
<!-- test_imp_cm <- list_systemData0$slrImpacts %>%  -->
<!--   mutate(model_fact = model_dot %>% fun_slrModel2Height(include="values", valType="factor",labelType="character")) -->
<!-- test_imp_cm %>% glimpse -->
<!-- test_imp_cm %>% filter(year > 2090) %>% filter(is.na(scaled_impacts)) %>% nrow -->
<!-- test_imp_cm %>% mutate(n=1) %>% group_by_at(.vars=c("year", "sector", "variant", "impactType", "impactYear", "region", "model")) %>% summarize_at(.vars=c("n"), sum) %>% filter(n>1) %>% nrow -->
<!-- ``` -->

<!-- Visual check of scaled impacts  -->

<!-- ```{r, fig.width=9, fig.height=5} -->
<!-- plots_imp_cm <- test_imp_cm %>%  -->
<!--   filter(year %in% seq(2000, 2300, by=10)) %>% -->
<!--   (function(data_x){ -->
<!--     sectors_x <- data_x$sector %>% unique -->
<!--     list_x    <- sectors_x %>% lapply(function(sector_i){ -->
<!--       ### Filter data -->
<!--       data_i <- data_x %>% filter(sector==sector_i) -->
<!--       # data_i <- data_i %>% mutate(variant=variant %>% as.character) -->
<!--       # var_i  <- data_i$variant %>% unique; var_i %>% print -->
<!--       ### Adjust data -->
<!--       lim_i  <- data_i$scaled_impact %>% min(na.rm=T) %>% c(data_i$scaled_impact %>% max(na.rm=T)) -->
<!--       rng_i  <- lim_i[2] - lim_i[1] -->
<!--       # c(lim_i) %>% print -->
<!--       ### Log -->
<!--       log_i  <- rng_i %>% log10 %>% floor %>% as.integer -->
<!--       ord_i  <- (log_i %/% 3) %>% floor %>% as.integer -->
<!--       div_i  <- (10e3)^ord_i -->
<!--       # c(rng_i, log_i, ord_i) %>% print -->
<!--       ### Scale limits -->
<!--       lim2_i <- c(floor(round(lim_i[1] / div_i, 3)), round(lim_i[2] / div_i, 3)) -->
<!--       rng2_i <- (lim2_i[2] - lim2_i[1]) -->
<!--       log2_i <-  rng2_i %>% log10 %>% floor %>% as.integer -->
<!--       c(lim2_i, rng2_i, log2_i) %>% print -->
<!--       ### -->
<!--       adj_i  <- ifelse(log2_i<0, -1, 1) %>% as.integer -->
<!--       adj2_i <- (adj_i*log2_i + 1)      %>% as.integer -->
<!--       adj3_i <- (10^as.integer(adj2_i)) %>% as.integer -->
<!--       c(adj_i, adj2_i, adj2_i) %>% print -->
<!--       ### Steps -->
<!--       stp1_i <- (rng2_i / 5)*10^adj2_i -->
<!--       stp2_i <- stp1_i %>% ceiling -->
<!--       stp3_i <- stp2_i / 10^(adj2_i + 0) -->

<!--       c(stp1_i, stp2_i, stp3_i) %>% print -->
<!--       ### Labs and breaks -->
<!--       yLab_i <- c("thousands", "millions", "billions")[ord_i] -->
<!--       brk_i  <- seq(lim2_i[1], lim2_i[2], by = stp3_i) %>% round(2) -->
<!--       lab_i  <- brk_i %>% as.character -->
<!--       c(yLab_i) %>% print; c(brk_i) %>% print; c(lab_i) %>% print -->
<!--       data_i <- data_i %>% mutate(scaled_impacts=scaled_impacts/div_i) -->
<!--       data_i <- data_i %>% mutate(scaled_impacts=scaled_impacts %>% round(6)) -->
<!--       #### Plot data -->
<!--       plot_i <- data_i %>% ggplot() + -->
<!--         geom_line(aes(x=year, y=scaled_impacts, group=interaction(impactType, variant, region), color = region, linetype=impactType), alpha = 0.4) + -->
<!--         facet_grid(.~model_fact) -->
<!--       plot_i <- plot_i + -->
<!--         theme(legend.position = "bottom") + -->
<!--         theme(axis.text.x = element_text(angle=90)) -->
<!--       plot_i <- plot_i + ggtitle(sector_i) -->
<!--       plot_i <- plot_i + scale_y_continuous(yLab_i, breaks = brk_i, labels=lab_i) -->
<!--       return(plot_i) -->
<!--     }) -->
<!--     names(list_x) <- sectors_x -->
<!--     return(list_x) -->
<!--   }) -->
<!-- plots_imp_cm[[1]] -->
<!-- ``` -->


<!-- #### SLR Scaled Extremes -->



<!-- ```{r} -->
<!-- frediPath %>% load_all -->
<!-- test_ext_cm <- fun_slrConfigExtremes( -->
<!--   slr_x = list_systemData0$slr_cm,    ### rDataList$slr_cm -->
<!--   imp_x = list_systemData0$slrImpacts ### rDataList$slrImpacts -->
<!-- ) -->
<!-- # test_ext_cm %>% filter(driverValue2 < driverValue1) %>% nrow -->
<!-- # test_ext_cm %>% filter(driverValue2 == driverValue1) %>% nrow -->
<!-- # test_ext_cm %>% filter(is.na(driverValue)) %>% nrow -->
<!-- test_ext_cm %>% filter(impacts_intercept < 0) %>% nrow -->
<!-- test_ext_cm %>% filter(impacts_slope     < 0) %>% nrow -->
<!-- test_ext_cm %>% glimpse -->
<!-- ``` -->


<!-- SLR scaled impacts should have no missing values past 2090 and only one row for each `year~sector~variant~impactType~impactYear~region~model` combo: -->


<!-- ```{r test_ext_cm} -->
<!-- # frediPath %>% load_all -->
<!-- test_ext_cm <- list_systemData0$slrExtremes #%>% mutate(model_fact = model_dot %>% fun_slrModel2Height(include="values", valType="factor",labelType="character")) -->
<!-- test_ext_cm %>% glimpse -->
<!-- test_ext_cm %>% filter(impacts_intercept < 0) %>% nrow -->
<!-- test_ext_cm %>% filter(impacts_slope < 0) %>% nrow -->
<!-- test_ext_cm %>% filter(year > 2090) %>% filter(is.na(impacts_slope)) %>% nrow -->
<!-- test_ext_cm %>% mutate(n=1) %>% group_by_at(.vars=c("year", "sector", "variant", "impactType", "impactYear", "region")) %>% summarize_at(.vars=c("n"), sum) %>% filter(n>1) %>% nrow -->
<!-- ``` -->


<!-- Check values -->

<!-- ```{r} -->
<!-- test_ext_cm %>% filter(impacts_slope < 0) %>% nrow -->

<!-- test_ext_cm %>% filter(impacts_slope %>% is.infinite) %>% nrow -->
<!-- ``` -->



<!-- Function to get breaks and limits -->

<!-- ```{r get_plotBreaks} -->
<!-- get_plotBreaks  <- function(col_x){ -->
<!--   lim_i  <- col_x %>% range(na.rm=T) -->
<!--   # lim_i %>% print -->
<!--   ### Do range  -->
<!--   doNull1 <- lim_i %>% range(na.rm=T) %>% is.infinite %>% any -->
<!--   doNull2 <- lim_i %>% range(na.rm=T) %>% is.na       %>% any -->
<!--   doNull3 <- lim_i[1] == lim_i[2] -->
<!--   doNull  <- doNull1 | doNull2 | doNull3 -->
<!--   if(doNull) { -->
<!--     "got here yay!" %>% print -->
<!--     lab_i <- brk_i <- yLab_i <- div_i <- lim_i <- NULL -->
<!--   } -->
<!--   else       { -->
<!--     rng_i  <- lim_i[2] - lim_i[1] -->
<!--     # "got here1.0" %>% print -->
<!--     # c(lim_i) %>% print -->

<!--     ### Log -->
<!--     log_i  <- rng_i %>% log10 %>% floor %>% as.integer -->
<!--     ord_i  <- (log_i %/% 3) %>% floor %>% as.integer -->
<!--     div_i  <- (10e3)^ord_i -->
<!--     # "got here1.1" %>% print -->
<!--     # c(rng_i, log_i, ord_i) %>% print -->

<!--     ### Scale limits -->
<!--     lim2_i <- c(floor(round(lim_i[1] / div_i, 3)), round(lim_i[2] / div_i, 3)) -->
<!--     rng2_i <- (lim2_i[2] - lim2_i[1]) -->
<!--     log2_i <-  rng2_i %>% log10 %>% floor %>% as.integer -->
<!--     # "got here1.2" %>% print -->
<!--     # c(lim2_i, rng2_i, log2_i) %>% print -->

<!--     ### Adjustment -->
<!--     # adj_i  <- ifelse(log2_i<0, -1, 1) %>% as.integer -->
<!--     adj2_i <- (abs(log2_i) + 1)       %>% as.integer -->
<!--     adj3_i <- (10^as.integer(adj2_i)) %>% as.integer -->
<!--     # "got here1.3" %>% print -->
<!--     # c(adj2_i, adj3_i) %>% print -->

<!--     ### Steps -->
<!--     stp1_i <- (rng2_i / 5)*10^adj2_i -->
<!--     stp2_i <- stp1_i %>% ceiling -->
<!--     stp3_i <- stp2_i / 10^(adj2_i + 0) -->
<!--     # c(stp1_i, stp2_i, stp3_i) %>% print -->
<!--     # "got here1.4" %>% print -->

<!--     ### Labs and breaks -->
<!--     yLab_i <- c("Thousands", "Millions", "Billions")[ord_i] -->
<!--     brk_i  <- seq(lim2_i[1], lim2_i[2], by = stp3_i) %>% round(2) -->
<!--     lab_i  <- brk_i %>% as.character -->
<!--     ### Limits -->
<!--     lim_i  <- lim_i / div_i -->
<!--     # c(yLab_i) %>% print; c(brk_i) %>% print; c(lab_i) %>% print -->
<!--   } -->
<!--   ### Return x -->
<!--   return_x <- list( -->
<!--     div    = div_i,  -->
<!--     yLab   = yLab_i,  -->
<!--     limits = lim_i,  -->
<!--     breaks = brk_i,  -->
<!--     labels = lab_i -->
<!--   ) -->
<!--   return(return_x) -->
<!-- } -->
<!-- ``` -->


<!-- Visual check of impacts -->

<!-- ```{r plots_ext_imp, fig.width=6, fig.height=4} -->
<!-- plots_ext_imp <- test_ext_cm %>%  -->
<!--   mutate(impact = impacts_intercept + impacts_slope * driverValue_ref) %>%  -->
<!--   mutate(value = impact) %>% -->
<!--   # filter(year %in% seq(2000, 2300, by=10)) %>% -->
<!--   (function(data_x, title = "SLR Impact Values"){ -->
<!--     sectors_x <- data_x$sector %>% unique -->
<!--     list_x    <- sectors_x %>% lapply(function(sector_i){ -->
<!--       # ySub   <- "SLR Impact Slopes" -->
<!--       ## Filter data -->
<!--       # data_i <- data_x -->
<!--       data_i <- data_x %>% filter(sector==sector_i) -->
<!--       # data_i$value %>% range(na.rm=TRUE) %>% print -->
<!--       # data_i <- data_i %>% mutate(variant=variant %>% as.character) -->
<!--       # var_i  <- data_i$variant %>% unique; var_i %>% print -->
<!--       ### Get breaks -->
<!--       list_i <- data_i$value %>% get_plotBreaks -->
<!--       list_i %>% print -->
<!--       # list_i[c("breaks", "labels")] %>% lapply(function(y){length(y)}) %>% unlist %>% print -->
<!--       ### Adjust data -->
<!--       rnd_i  <- list_i$div %>% log10 %>% abs -->
<!--       data_i <- data_i %>% mutate(value=value/list_i$div) -->
<!--       # data_i <- data_i %>% mutate(value=value %>% round(rnd_i)) -->
<!--       #### Plot data -->
<!--       plot_i <- data_i %>% ggplot() + geom_line(aes(x=year, y=value, group=interaction(impactType, variant, region), color = region, linetype=impactType), alpha = 0.4) + -->
<!--         facet_grid(.~region) -->
<!--       plot_i <- plot_i + theme(legend.position = "bottom") + theme(axis.text.x = element_text(angle=90)) -->
<!--       plot_i <- plot_i + ggtitle(title) -->
<!--       # plot_i <- plot_i + scale_y_continuous(list_i$yLab, limits=list_i$limits, breaks = list_i$breaks, labels=list_i$labels) -->
<!--       plot_i <- plot_i + scale_y_continuous() -->
<!--       return(plot_i) -->
<!--     }) -->
<!--     names(list_x) <- sectors_x -->
<!--     return(list_x) -->
<!--   }) -->
<!-- plots_ext_imp -->
<!-- ``` -->



<!-- Visual check of extreme impact driver values -->



<!-- ```{r plots_ext_cm, fig.width=6, fig.height=4} -->
<!-- plots_ext_cm <- test_ext_cm %>%  -->
<!--   mutate(value = driverValue_ref) %>% -->
<!--   group_by_at(.vars=c("year")) %>% summarize_at(.vars = c("value"), mean) %>%  -->
<!--   filter(year %in% seq(2000, 2300, by=10)) %>% -->
<!--   (function(data_x, title = "Maximum Driver Value"){ -->
<!--     # sectors_x <- data_x$sector %>% unique -->
<!--     # list_x    <- sectors_x %>% lapply(function(sector_i){ -->
<!--     ### Standardize value column -->
<!--     # data_x <- data_x %>% mutate(value = driverValue_ref) -->
<!--     # ySub   <- "Maximum Driver Value" -->
<!--     ### Filter data -->
<!--     data_i <- data_x -->
<!--     # data_i <- data_x %>% filter(sector==sector_i) -->
<!--     # data_i <- data_i %>% mutate(variant=variant %>% as.character) -->
<!--     # var_i  <- data_i$variant %>% unique; var_i %>% print -->
<!--     ### Get breaks -->
<!--     list_i <- data_i$value %>% get_plotBreaks -->
<!--     list_i %>% print -->
<!--     # list_i[c("breaks", "labels")] %>% lapply(function(y){length(y)}) %>% unlist %>% print -->
<!--     ### Adjust data -->
<!--     rnd_i  <- list_i$div %>% log10 %>% abs -->
<!--     data_i <- data_i %>% mutate(value=value/list_i$div) -->
<!--     data_i <- data_i %>% mutate(value=value %>% round(rnd_i)) -->
<!--     #### Plot data -->
<!--     plot_i <- data_i %>% ggplot() +geom_line(aes(x=year, y=value), alpha = 0.4) -->
<!--     plot_i <- plot_i + theme(legend.position = "bottom") + theme(axis.text.x = element_text(angle=90)) -->
<!--     plot_i <- plot_i + ggtitle(title) -->
<!--     plot_i <- plot_i + scale_y_continuous(list_i$yLab, limits=list_i$limits, breaks = list_i$breaks, labels=list_i$labels) -->
<!--     return(plot_i) -->
<!--     # }) -->
<!--     # names(list_x) <- sectors_x -->
<!--     # return(list_x) -->
<!--   }) -->
<!-- plots_ext_cm -->
<!-- ``` -->


<!-- Visual check of intercepts -->

<!-- ```{r plots_ext_int, fig.width=6, fig.height=4} -->
<!-- plots_ext_int <- test_ext_cm %>%  -->
<!--   mutate(value = impacts_intercept) %>% -->
<!--   filter(year %in% seq(2000, 2300, by=10)) %>% -->
<!--   (function(data_x, title = "SLR Impact Intercepts"){ -->
<!--     sectors_x <- data_x$sector %>% unique -->
<!--     list_x    <- sectors_x %>% lapply(function(sector_i){ -->
<!--       ySub   <- "SLR Impact Intercepts" -->
<!--       ## Filter data -->
<!--       data_i <- data_x %>% filter(sector==sector_i) -->
<!--       # data_i$value %>% range %>% print -->
<!--       # data_i <- data_i %>% mutate(variant=variant %>% as.character) -->
<!--       # var_i  <- data_i$variant %>% unique; var_i %>% print -->
<!--       ### Get breaks -->
<!--       list_i <- data_i$value %>% get_plotBreaks -->
<!--       # list_i %>% print -->
<!--       ### Adjust data -->
<!--       rnd_i  <- list_i$div %>% log10 %>% abs -->
<!--       data_i <- data_i %>% mutate(value=value/list_i$div) -->
<!--       # data_i <- data_i %>% mutate(value=value %>% round(rnd_i)) -->
<!--       #### Plot data -->
<!--       plot_i <- data_i %>% ggplot() + geom_line(aes(x=year, y=value, group=interaction(impactType, variant, region), color = region, linetype=impactType), alpha = 0.4) + -->
<!--         facet_grid(.~region) -->
<!--       plot_i <- plot_i + theme(legend.position = "bottom") + theme(axis.text.x = element_text(angle=90)) -->
<!--       plot_i <- plot_i + ggtitle(title) -->
<!--       plot_i <- plot_i + scale_y_continuous(list_i$yLab, limits=list_i$limits, breaks = list_i$breaks, labels=list_i$labels) -->
<!--       return(plot_i) -->
<!--     }) -->
<!--     names(list_x) <- sectors_x -->
<!--     return(list_x) -->
<!--   }) -->
<!-- plots_ext_int -->
<!-- ``` -->


<!-- Visual check of slopes -->

<!-- ```{r plots_ext_slope, fig.width=6, fig.height=4} -->
<!-- plots_ext_slope <- test_ext_cm %>%  -->
<!--   mutate(value = impacts_slope) %>% -->
<!--   filter(year %in% seq(2000, 2300, by=10)) %>% -->
<!--   (function(data_x, title = "SLR Impact Slope"){ -->
<!--     sectors_x <- data_x$sector %>% unique -->
<!--     list_x    <- sectors_x %>% lapply(function(sector_i){ -->
<!--       ySub   <- "SLR Impact Slope" -->
<!--       ## Filter data -->
<!--       # data_i <- data_x -->
<!--       data_i <- data_x %>% filter(sector==sector_i) -->
<!--       data_i$value %>% range %>% print -->
<!--       # data_i <- data_i %>% mutate(variant=variant %>% as.character) -->
<!--       # var_i  <- data_i$variant %>% unique; var_i %>% print -->
<!--       ### Get breaks -->
<!--       list_i <- data_i$value %>% get_plotBreaks -->
<!--       # list_i %>% print -->
<!--       # list_i[c("breaks", "labels")] %>% lapply(function(y){length(y)}) %>% unlist %>% print -->
<!--       ### Adjust data -->
<!--       rnd_i  <- list_i$div %>% log10 %>% abs -->
<!--       data_i <- data_i %>% mutate(value=value/list_i$div) -->
<!--       # data_i <- data_i %>% mutate(value=value %>% round(rnd_i)) -->
<!--       #### Plot data -->
<!--       plot_i <- data_i %>% ggplot() + geom_line(aes(x=year, y=value, group=interaction(impactType, variant, region), color = region, linetype=impactType), alpha = 0.4) + -->
<!--         facet_grid(.~region) -->
<!--       plot_i <- plot_i + theme(legend.position = "bottom") + theme(axis.text.x = element_text(angle=90)) -->
<!--       plot_i <- plot_i + ggtitle(title) -->
<!--       plot_i <- plot_i + scale_y_continuous(list_i$yLab, limits=list_i$limits, breaks = list_i$breaks, labels=list_i$labels) -->
<!--       return(plot_i) -->
<!--     }) -->
<!--     names(list_x) <- sectors_x -->
<!--     return(list_x) -->
<!--   }) -->
<!-- plots_ext_slope -->
<!-- ``` -->



<!-- Visual check of intercepts versus driver value -->

<!-- ```{r, fig.width=6, fig.height=4} -->
<!-- plots_ext_slope <- test_ext_cm %>%  -->
<!--   mutate(value = impacts_slope) %>% -->
<!--   filter(year %in% seq(2000, 2300, by=10)) %>% -->
<!--   (function(data_x, title = "SLR Impact Slopes"){ -->
<!--     sectors_x <- data_x$sector %>% unique -->
<!--     list_x    <- sectors_x %>% lapply(function(sector_i){ -->
<!--       # ySub   <- "SLR Impact Slopes" -->
<!--       ## Filter data -->
<!--       data_i <- data_x %>% filter(sector==sector_i) -->
<!--       # data_i$value %>% range %>% print -->
<!--       # data_i <- data_i %>% mutate(variant=variant %>% as.character) -->
<!--       # var_i  <- data_i$variant %>% unique; var_i %>% print -->
<!--       ### Get breaks -->
<!--       list_i <- data_i$value %>% get_plotBreaks -->
<!--       # list_i %>% print -->
<!--       ### Adjust data -->
<!--       rnd_i  <- list_i$div %>% log10 %>% abs -->
<!--       data_i <- data_i %>% mutate(value=value/list_i$div) -->
<!--       # data_i <- data_i %>% mutate(value=value %>% round(rnd_i)) -->
<!--       #### Plot data -->
<!--       plot_i <- data_i %>% ggplot() + geom_line(aes(x=driverValue_ref, y=value, group=interaction(impactType, variant, region), color = region, linetype=impactType), alpha = 0.4) + -->
<!--         facet_grid(.~region) -->
<!--       plot_i <- plot_i + theme(legend.position = "bottom") + theme(axis.text.x = element_text(angle=90)) -->
<!--       plot_i <- plot_i + ggtitle(title) -->
<!--       plot_i <- plot_i + scale_y_continuous(list_i$yLab, limits=list_i$limits, breaks = list_i$breaks, labels=list_i$labels) -->
<!--       return(plot_i) -->
<!--     }) -->
<!--     names(list_x) <- sectors_x -->
<!--     return(list_x) -->
<!--   }) -->
<!-- plots_ext_slope -->
<!-- ``` -->


<!-- Visual check of slopes -->

<!-- ```{r, fig.width=6, fig.height=4} -->
<!-- plots_ext_slDriv <- test_ext_cm %>%  -->
<!--   mutate(value = impacts_slope) %>% -->
<!--   filter(year %in% seq(2000, 2300, by=10)) %>% -->
<!--   (function(data_x, title = "SLR Impact Slopes"){ -->
<!--     sectors_x <- data_x$sector %>% unique -->
<!--     list_x    <- sectors_x %>% lapply(function(sector_i){ -->
<!--       ySub   <- "SLR Impact Slopes" -->
<!--       ## Filter data -->
<!--       # data_i <- data_x -->
<!--       data_i <- data_x %>% filter(sector==sector_i) -->
<!--       data_i$value %>% range %>% print -->
<!--       # data_i <- data_i %>% mutate(variant=variant %>% as.character) -->
<!--       # var_i  <- data_i$variant %>% unique; var_i %>% print -->
<!--       ### Get breaks -->
<!--       list_i <- data_i$value %>% get_plotBreaks -->
<!--       list_i %>% print -->
<!--       # list_i[c("breaks", "labels")] %>% lapply(function(y){length(y)}) %>% unlist %>% print -->
<!--       ### Adjust data -->
<!--       rnd_i  <- list_i$div %>% log10 %>% abs -->
<!--       data_i <- data_i %>% mutate(value=value/list_i$div) -->
<!--       # data_i <- data_i %>% mutate(value=value %>% round(rnd_i)) -->
<!--       #### Plot data -->
<!--       plot_i <- data_i %>% ggplot() + geom_line(aes(x=driverValue_ref, y=value, group=interaction(impactType, variant, region), color = region, linetype=impactType), alpha = 0.4) + -->
<!--         facet_grid(.~region) -->
<!--       plot_i <- plot_i + theme(legend.position = "bottom") + theme(axis.text.x = element_text(angle=90)) -->
<!--       plot_i <- plot_i + ggtitle(title) -->
<!--       plot_i <- plot_i + scale_y_continuous(list_i$yLab, limits=list_i$limits, breaks = list_i$breaks, labels=list_i$labels) -->
<!--       return(plot_i) -->
<!--     }) -->
<!--     names(list_x) <- sectors_x -->
<!--     return(list_x) -->
<!--   }) -->
<!-- plots_ext_slDriv -->
<!-- ``` -->






<!-- #### GCM Functions -->

<!-- Check GCM impact functions: -->

<!-- ```{r test_impactVals1} -->
<!-- test_impactVals1 <- -1:20 -->
<!-- ``` -->


<!-- Regions -->


<!-- ```{r test_co_regions} -->
<!-- test_co_regions <- list_systemData0$co_regions; test_co_regions -->
<!-- ``` -->


<!-- Examine model types -->

<!-- ```{r} -->
<!-- list_systemData0$co_models %>% glimpse -->
<!-- list_systemData0$co_modelTypes %>% glimpse -->
<!-- ``` -->



<!-- Model types -->

<!-- ```{r test_co_models} -->
<!-- test_co_models  <- list_systemData0$co_models %>% select(c("model_dot", "modelType")); test_co_models %>% glimpse -->
<!-- test_models_dot <- (test_co_models %>% filter(modelType %in% c("gcm")))$model_dot; test_models_dot -->
<!-- test_gcm_impact <- list_systemData0$list_impactFunctions[1:1e3]; test_gcm_impact %>% head %>% names -->
<!-- test_gcm_names  <- test_gcm_impact %>% names; test_gcm_names %>% head -->
<!-- # test_gcm_names[30:60] -->
<!-- ``` -->


<!-- * GISS-E2-R defined up to 3 degrees of warming: Should have NA values for values above 3 degrees -->
<!-- * GFDL-CM3 defined up to 6 degrees of warming: : Should have same values for values 10C and above -->

<!-- ```{r test_gcm_impacts} -->
<!-- # test_gcm_impact[["ATSExtremeTemp_high_CI_NA_NA_gcm_CCSM4_Northeast"]](-1) -->
<!-- ### function(str_x, vals_x=test_impactVals1, data_x=test_gcm_impact, models_x=test_models_dot) -->
<!-- test_gcm_impacts <- test_co_regions$region_dot %>% lapply(function(region_j){ -->
<!--   df_j <- test_models_dot  %>% lapply(function( -->
<!--     model_i,  -->
<!--     sector_i = "ATSExtremeTemp", -->
<!--     variant_i = "high_CI", -->
<!--     impType_i = "NA", -->
<!--     impYear_i = "NA"){ -->
<!--     ### String -->
<!--     str_x    <- paste(sector_i, variant_i, impType_i, impYear_i, "gcm", sep="_");  -->
<!--     ### Region and name -->
<!--     region_i <- region_j -->
<!--     name_i   <- paste(str_x, model_i, region_i, sep="_");  -->
<!--     check_i  <- (name_i %in% test_gcm_names) -->

<!--     # paste0(name_i, ": ", check_i) %>% print -->
<!--     df_i     <- data.frame(driverValue   = test_impactVals1, scaled_impacts = NA) -->
<!--     df_i     <- df_i %>% mutate(model_id = model_i) -->
<!--     df_i     <- df_i %>% mutate(region   = region_i) -->
<!--     df_i     <- df_i %>% mutate(func_id  = str_x) -->
<!--     df_i     <- df_i %>% mutate(scaled_impacts = NA) -->
<!--     str_x="ATSExtremeTemp_high_CI_NA_NA_gcm" -->
<!--     if(check_i){ -->
<!--       fun_i  <- test_gcm_impact[[name_i]] -->
<!--       vals_i <- fun_i(df_i$driverValue) -->
<!--       df_i   <- df_i %>% mutate(scaled_impacts = vals_i) -->
<!--     } -->
<!--     return(df_i) -->
<!--   }) %>% (function(df_i){do.call(rbind, df_i)}) -->
<!-- }) %>% (function(df_j){do.call(rbind, df_j)}) -->

<!-- test_gcm_impacts %>% glimpse -->
<!-- ``` -->


<!-- View Impacts -->

<!-- ```{r, fig.height=5, fig.width=9} -->
<!-- test_gcm_impacts %>%  -->
<!--   mutate(scaled_impacts = scaled_impacts %>% round(6)) %>% -->
<!--   ggplot() +  -->
<!--   geom_line(aes(x=driverValue, y =scaled_impacts, color = region)) + facet_grid(.~model_id) + -->
<!--   # geom_line(aes(x=driverValue, y =scaled_impacts, color = model_id)) + facet_grid(.~region) +  -->
<!--   scale_y_continuous(breaks = seq(0, 5, by=1)*5e-4, labels = (seq(0, 5, by=1)*5e-4) %>% as.character) + -->
<!--   theme(legend.position = "bottom") -->
<!-- ``` -->


