---
title: "Configure R Tool Data"
author: "Industrial Economics, Inc."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_document:
    theme: spacelab
    toc: true
    toc_float: true
---

<style>
/* Simplified version of Bootstrap's responsive table CSS */
.table-responsive {
    display: block;
    width: 100%;
    overflow-x: auto;
}

.table-responsive > table {
    width: 100%;
}
</style>


```{r knitr setup, include=FALSE}
### The following parameters declare the options for compiling the Markdown document.
knitr::opts_chunk$set(
  include = T,     ### Evaluate and depict outputs of code chunks in the compiled document
  echo    = T,     ### Echo the commands of the code chunks in the compiled document
  message = FALSE, ### Don't include command-line messages output from evaluating code chunks
  cache   = FALSE, ### Don't cache the evaluation of code chunks
  warning = FALSE,  ### Don't include warnings from evaluating code chunks
  table.format = "html" 
)
```

## Overview

The purpose of this package is to configure the R tool

Load packages 

```{r loadPackages}
### Packages
require(tidyverse)
require(openxlsx)
require(devtools)
```


Paths



```{r declare paths}
### Set system paths
projectPath      <- getwd()
today            <- format(Sys.Date(), "%Y%m%d")
### Code path
codePath         <- projectPath %>% paste("R", sep="/")
codeNames        <- codePath %>% list.files(".R")
### FrEDI path
frediPath        <- projectPath %>% file.path("..", "FrEDI")
```


## Create SV Configuration Data


Load configuration functions

```{r load config}
### Load all functions
codeNames; for(name_i in codeNames){ 
  name_i %>% print
  source(paste(codePath, name_i, sep="/")) 
}

```

Test system data



```{r test_systemData0}
for(name_i in codeNames){ source(paste(codePath, name_i, sep="/")) }
### "Air Quality", "Extreme Temperature", "Labor", "Roads", "High Tide Flooding and Traffic", "Coastal Properties"
test_sector <- c("Air Quality")
### Uncomment following two lines to create and save data and check the outputs
time1           <- Sys.time()
# test_svData     <- createSVData(save=T, sv = T, pop = T)
# test_svData     <- createSVData(save=T, sv = F, pop=T)
# test_svData     <- createSVData(save=T, sv = F, pop=F, impacts = T, impactSectors = test_sector, format=F)
test_svData     <- createSVData(save=T, sv = F, format=T)
time2           <- Sys.time()
time_create     <- time2 - time1; time_create
```



Update system data

```{r}
for(name_i in codeNames){ source(paste(codePath, name_i, sep="/")) }
# admisc::obj.rda(file.path(frediPath, "R", "svDataList.rda"))
# admisc::obj.rda(file.path(frediPath, "R", "svPopData.rda"))
# admisc::obj.rda(file.path(frediPath, "R", "format_styles.rda"))
update_sysdata(sv=T, impacts=F, save=T)
```

Check formats


```{r}
for(name_i in codeNames){ source(paste(codePath, name_i, sep="/")) }
test_svData     <- createSVData(save=T, sv = F, format=T)
# load(file.path(projectPath, "data", "sv", "format_styles.rda"))
# format_styles %>% glimpse
```





Use the following code chunk to view/check outputs for the new sector (all data stored in a list called `test_systemData`)

```{r check outputs}

# test_svData$svDataList$
# test_svData$svDataList$svData$race_amInd %>% class
# test_svData$svDataList$svDataCoastal$race_amInd %>% class
# test_svData$svDataList$svDataCoastal %>% filter(is.nan(race_amInd)) %>% nrow

load(file.path(projectPath, "data", "sv", "svPopData.rda"))
load(file.path(projectPath, "data", "sv", "svDataList.rda"))
load(file.path(projectPath, "data", "sv", "svPopData.rda"))

# load(file.path(projectPath, "data", "sv", "impactsList_coastalProp_withAdapt.rda"))
load(file.path(projectPath, "data", "sv", "impactsLists", "impactsList_airQuality.rda"))


# other_tracts <- svDataList$svData$fips %>% unique
# other_tracts %>% length
# other_tracts %>% head
# 
# 
# 
# coastal_tracts <- svDataList$svDataCoastal$fips %>% unique
# coastal_tracts %>% length
# coastal_tracts %>% head
# 
# imp_tracts <- impactsList_coastalProp_withAdapt %>% names
# imp_tracts %>% length
# imp_tracts %>% head
```


Look at `svTestData` (17,824 rows, 22 columns):

* 17824 unique ids
* 318 unique geoids or 300 unique geoids


```{r svTestData}
### Standardize names
# svTestData <- svDataList$svDataCoastal %>%
#   mutate(nChar  = fips %>% nchar) %>%
#   mutate(fips2  = paste0(ifelse(nChar > 11, "", 0), fips)) %>%
#   mutate(nChar2 = fips2 %>% nchar) %>%
#   mutate(geoid102 = fips2 %>% substr(1, 5))
# svTestData <- svDataList$svDataCoastal
svTestData <- svDataList$svData
svTestData %>% glimpse
```

Information about the ids and regions for `svDataCoastal`:

* 17824 unique FIPS
* 300 unique geoids

```{r}
svTestData$region %>% unique
test_sv_fips  <- svTestData$fips     %>% unique; test_sv_fips  %>% (function(x){paste0(length(x), ": ", paste(head(x), collapse=", "))})
test_sv_geos  <- svTestData$geoid10  %>% unique; test_sv_geos  %>% (function(x){paste0(length(x), ": ", paste(head(x), collapse=", "))})
# svTestData$nChar %>% range %>% c(svTestData$nChar2 %>% range)
# test_sv_geos2 <- svTestData$geoid102 %>% unique; test_sv_geos2 %>% (function(x){paste0(length(x), ": ", paste(head(x), collapse=", "))})
```


### Test Population

Create county projections (59014 rows, 9 columns):


```{r test pop}
### Load function and `svPopList`
# frediPath %>% file.path("R", "utils_sv.R") %>% source
# # load_all(frediPath)
# load(file.path(frediPath, "R", "svPopData.rda"))
test_pop <- 
    calc_countyPop(
      regPop  = svPopList$iclus_region_pop,
      funList = svPopList$popProjList,
      years   = seq(2010, 2090, by=5)
    ); 
test_pop %>% glimpse
```

Examine test population info:

* 3106 unique geoids
* 270 / 3106 geoids in `svDataCoastal`

```{r}
test_pop$region %>% unique
test_pop_geos <- test_pop$geoid10 %>% unique; test_pop_geos %>% (function(x){paste0(length(x), ": ", paste(head(x), collapse=", "))})
test_pop_geos[test_pop_geos %in% test_sv_geos] %>% length ### All 300 ids present
```



Join with `svDataCoastal` (318460 rows):

```{r popCoastal}
popCoastal <- svTestData %>% left_join(test_pop, by = c("region", "state", "geoid10"))
popCoastal %>% glimpse
```


Check whether there are any missing values: 39 missing population values. 

* 1122 missing values, 39 tracts with missing information
* All missing values are in Virginia
* Missing values have the the same as those already missing in the population projections. Checks out!

```{r df_check_na_pop}
df_check_na_pop <- popCoastal %>% filter(is.na(county_pop))
df_check_na_pop %>% nrow
(df_check_na_pop %>% nrow) == (popCoastal %>% filter(is.na(county_pop)) %>% nrow)

df_check_na_pop$state %>% unique

df_check_na_pop_ids <- df_check_na_pop$geoid10 %>% unique
df_check_na_pop_ids %>% length
(df_check_na_pop_ids %in% ((popCoastal %>% filter(is.na(county_pop)))$geoid10 %>% unique)) %>% all
# df_check_na_pop_ids
```


Check for the impact projections (174 720 rows)

```{r impCoastal}
# load(file.path(frediPath, "sv", "impactsList_coastalProp_withAdapt.rda"))
impCoastal <- calc_tractScaledImpacts(
        # funList      = impactsList_coastalProp_withAdapt,
  funList      = impactsList_airQuality,
  driverValues = svDataList$gcamScenarios %>% 
    filter(scenario == "ECS_3.0_ref_0") %>% 
    select(c("year", "temp_C_conus")) %>%
    rename(driverValue = temp_C_conus) %>%
    mutate(driverUnit = "degrees Celsius")
)
impCoastal %>% glimpse
```

Examine missing info: No missing values

* Impacts data has 1920 unique FIPS
* Compare with SV block group data with 17824 unique values

```{r df_check_na_imp}
df_check_na_imp <- impCoastal %>% filter(is.na(sv_impact)); df_check_na_imp %>% nrow
ids_imp_na      <- df_check_na_imp$fips %>% unique; ids_imp_na %>% length

test_imp_fips   <- impCoastal$fips %>% unique; test_imp_fips %>% (function(x){paste0(length(x), ": ", paste(head(x), collapse=", "))})
test_sv_fips %>% (function(x){paste0(length(x), ": ", paste(head(x), collapse=", "))})
```

Join with population info: 318 460 rows...same as `popCoastal`

```{r}
popImp <- popCoastal %>% left_join(impCoastal, by = c("year", "fips"))
popImp %>% glimpse
```


Check for missing values:

* 281980 rows with missing data
* 15904 unique FIPS with missing data

```{r df_combined_na}
df_combined_na <- popImp %>% filter(is.na(sv_impact))
df_combined_na %>% nrow
ids_combined_na <- df_combined_na$fips %>% unique
ids_combined_na %>% length
```

Check for non-missing values:

* 36480 rows
* 1920 unique FIPS with non-missing data...matches those with population information

```{r df_combined_notna}
df_combined_notna <- popImp %>% filter(!is.na(sv_impact))
df_combined_notna %>% nrow
ids_combined_notna <- df_combined_notna$fips %>% unique
ids_combined_notna %>% length
```

## Update R Tool

**Manually update the sysdata.rdata file in the Rtool.**

After copying and pasting the system data to the Rtool, try detaching the package and then loading the package functions. 


Try the package: 167,184 rows

```{r df_defaults, message=T}
# frediPath %>% list.files()
frediPath %>% load_all
test_sv <- run_fredi_sv(sector="Coastal Properties", projectPath=frediPath)
test_sv %>% glimpse
```








