---
title: "Configure R Tool Data"
author: "Industrial Economics, Inc."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_document:
    theme: spacelab
    toc: true
    toc_float: true
---

<style>
/* Simplified version of Bootstrap's responsive table CSS */
.table-responsive {
    display: block;
    width: 100%;
    overflow-x: auto;
}

.table-responsive > table {
    width: 100%;
}
</style>


```{r knitr setup, include=FALSE}
### The following parameters declare the options for compiling the Markdown document.
knitr::opts_chunk$set(
  include = T,     ### Evaluate and depict outputs of code chunks in the compiled document
  echo    = T,     ### Echo the commands of the code chunks in the compiled document
  message = FALSE, ### Don't include command-line messages output from evaluating code chunks
  cache   = FALSE, ### Don't cache the evaluation of code chunks
  warning = FALSE,  ### Don't include warnings from evaluating code chunks
  table.format = "html" 
)
```

## Overview

The purpose of this package is to configure the R tool

Load packages 

```{r loadPackages}
### Packages
require(tidyverse)
require(openxlsx)
require(devtools)
```


Date of most recent version of the Excel configuration file:

```{r mostRecentDate}
mostRecentDate <- "20220907"
```



```{r declare paths}
### Set print options
options(digits = 20)
### Set system paths
# projectPath      <- getwd()
projectPath      <- "."
today            <- format(Sys.Date(), "%Y%m%d")

### Path to fredi project
projectParentDir <- projectPath %>% file.path("..")
projectParentDir %>% list.files
frediPath        <- projectParentDir %>% file.path("FrEDI")

### Project configuration
configPath       <- projectPath %>% file.path("config")
# configFiles      <- configPath %>% list.files(".R")
configFiles      <- "frediConfig.R"
### Code path
codePath         <- projectPath %>% file.path("R")
codeNames        <- codePath %>% list.files(".R")
configLogPath    <- codePath %>% file.path("configLog")

### Names for archive and use versions
configFileName   <- "fredi_config"
configArchName   <- configLogPath %>% file.path(configFileName) %>% paste(today, sep="_") %>% paste0(".rda")
configUseName    <- codePath %>% file.path(configFileName) %>% paste0(".rda")

### Output path
dataOutPath      <- projectPath %>% file.path("data")
dataOutLog       <- dataOutPath %>% file.path("dataLog")
sysFileName      <- "sysdata"
sysArchName      <- dataOutLog %>% file.path(sysFileName) %>% paste(today, sep="_") %>% paste0(".rda")
excelFileName    <- mostRecentDate %>% paste("FrEDI_config.xlsx", sep="_")
sysUseName       <- dataOutPath %>% file.path(sysFileName) %>% paste0(".rda")
```

### Configuration Files

Load all configuration functions

```{r load config}
### Load all functions
configFiles; for(i in configFiles){ source(paste(configPath, i, sep="/")) }
```


List configuration files

```{r}
configLogPath %>% list.files("rda") %>% sort(decreasing=FALSE) %>% head
```

Update archive:

```{r}
frediConfig(outPath = configArchName)
```

Confirm copy was saved:

```{r}
basename(configArchName) %in% (configLogPath %>% list.files("rda"))
```

## Create Tool Configuration Data


Load all R functions and configuration files

```{r load config}
### Load all functions
codeNames; for(i in codeNames){ source(paste(codePath, i, sep="/")) }
```

Test system data

```{r test_systemData0}
frediPath %>% load_all
### Uncomment following two lines to create and save data and check the outputs
time1           <- Sys.time()
test_systemData <- createSystemData(save=F, excelName = excelFileName, silent=T)
time2           <- Sys.time()
time_create     <- time2 - time1; time_create
```


Use the following code chunk to view/check outputs for the new sector (all data stored in a list called `test_systemData`)

Well, none of the SLR impacts are not not missing past 2100 so there's that...

```{r}
test_systemData$slrImpacts %>% names
test_systemData$slrImpacts %>% filter(year > 2100) %>% filter(!is.na(scaled_impacts)) %>% nrow
```

But the SLR driver values appear to be ok (1400 out of 1400 are not missing)

```{r}
test_systemData$slr_cm %>% names
test_systemData$slr_cm %>% filter(year > 2100) %>% nrow
test_systemData$slr_cm %>% filter(year > 2100) %>% filter(!is.na(driverValue)) %>% nrow
```


Check GCM impact functions:
GISS-E2-R defined up to 3 degrees of warming. GFDL-CM3 defined up to 6 degrees of warming. 

```{r check outputs}
test_impactVals1 <- c(-1, 2:4, 10:11)
test_impactVals2 <- c(-1, 5:7, 10:11)
test_impactVals1 %>% test_systemData$list_impactFunctions$Labor_NA_NA_LostWages_gcm_GISS.E2.R_Midwest()
test_impactVals2 %>% test_systemData$list_impactFunctions$Labor_NA_NA_LostWages_gcm_GFDL.CM3_Midwest()

```





If above works, overwrite previous config

```{r save and overwrite data}
### Uncomment following two lines to create and save data and check the outputs
time1           <- Sys.time()
test_systemData <- createSystemData(save=T, excelName = excelFileName, outPath = sysArchName)
test_systemData <- createSystemData(save=T, excelName = excelFileName, silent=T)
time2           <- Sys.time()
time_create     <- time2 - time1; time_create
```







**Manually update the sysdata.rda file in the Rtool.**

After copying and pasting the system data to the Rtool, try detaching the package and then loading the package functions. 

```{r file.copy}
file.copy(
  from = dataOutPath %>% file.path(sysFileName) %>% paste0(".rda"),
  to   = frediPath   %>% file.path("R", sysFileName) %>% paste0(".rda"),
  overwrite = T
)
```


## Update SV

Use the following code to compile the SV configuration data

```{r test createSVData}
#for(name_i in codeNames){ source(paste(codePath, name_i, sep="/")) }
### "Air Quality", "Extreme Temperature", "Labor", "Roads", "High Tide Flooding and Traffic", "Coastal Properties"
#test_sector     <- c("Coastal Properties")
### Uncomment following two lines to create and save data and check the outputs
#time1           <- Sys.time()
#test_svData     <- createSVData(save=T, sv = T, pop = F, impacts=F, format=T)
# test_svData     <- createSVData(save=T, sv = F, format=F, impacts=T, impactSectors = test_sector)
#time2           <- Sys.time()
#time_create     <- time2 - time1; time_create
```



Use the following code to update the FrEDI system data with the SV data

```{r update_sysdata}
for(name_i in codeNames){ source(paste(codePath, name_i, sep="/")) }
update_sysdata(sv=T, impacts=F, save=T)
```


After running, [update the R tool](#updateRtool).


## Test R Tool

Change the following code if there are new sectors

```{r new_sectors}
# c_sectorsList <- FrEDI::get_sectorInfo()
c_sectorsList <- c("ATS Extreme Temperature", "Coastal Properties")
```


Test inputs

```{r}
### Values above maximum values
testInputs1 <- list(
  tempInput = data.frame( year = 2000:2300, temp_C = 11),
  slrInput  = data.frame( year = 2000:2300, slr_cm = 260)
  )
### Values below minimum
testInputs2 <- list(
  tempInput = data.frame(year = 2000:2020, temp_C = 1) %>% 
    rbind(data.frame(year=2021:2300, temp_C = -1))
)
```


```{r df_defaults, message=T}
### Results are fine for ATS Extreme Temperature and Coastal Properties
frediPath %>% load_all
test1 <- testInputs1 %>% run_fredi(sectorList = c_sectorsList, aggLevels="all")
test1$driverUnit %>% unique
test1 %>% filter(is.infinite(annual_impacts)) %>% nrow()
check1 <- test1 %>% filter(driverUnit=="cm", region=="Northeast"); check1 %>% head
(test1 %>% filter(driverUnit=="cm", region=="Northeast"))$model %>% unique
test1 %>% filter(is.na(annual_impacts)) %>% nrow()
check1 <- test1 %>% filter(is.na(annual_impacts))
### @Temp=4: -131031543004.56610107  518117915169.87200928; @Temp = 10: -131031543004.56610107  518117915169.87200928
test1 %>% filter(driverValue >3) %>% filter(model == "GISS-E2-R")  %>% select(annual_impacts) %>% as.vector %>% range(na.rm=T)
```


Try plotting

```{r}
test1 %>% filter(driverUnit=="cm", region=="Northeast") %>% ggplot() + geom_line(aes(x=year, y=annual_impacts, color=variant))
```


```{r}
frediPath %>% load_all
test2 <- testInputs2 %>% run_fredi(sectorList = c_sectorsList, aggLevels="none")
test2 %>% filter(is.infinite(annual_impacts)) %>% nrow
test2 %>% filter(is.na(annual_impacts)) %>% nrow
test2 %>% filter(driverValue <0) %>% filter(model == "GISS-E2-R") %>% select(annual_impacts) %>% as.vector %>% range(na.rm=T)
test2 %>% filter(driverValue <0) %>% select(annual_impacts) %>% as.vector %>% range(na.rm=T)
```




Try the package: 167,184 rows

```{r df_defaults, message=T}
frediPath %>% load_all
df_defaults <- run_fredi(sectorList = c_sectorsList, aggLevels=c("national", "modelaverage", "impactyear")) %>% filter(year %in% seq(2010, 2300, by=5)) 
# df_defaults <- FrEDI::run_fredi(sectorList = c_sectorsList, aggLevels="none") %>% filter(year %in% seq(2010, 2090, by=5))
df_defaults %>% filter(sector=="ATS Extreme Temperature") %>% filter(region=="National Total") %>% filter(year==2090) %>% filter(model=="Average")
df_defaults %>% dim
df_defaults %>% filter(!is.na(annual_impacts)) %>% nrow
(df_defaults %>% filter(!is.na(annual_impacts)))$annual_impacts %>% range
(df_defaults %>% filter(!is.na(annual_impacts)))$sector %>% unique
```



Examine rounding

```{r}
# Extreme Temperature, No Adaptation, 2090 socioeconomics, Cold, Midwest, CanESM2, 2070
# sprintf(x, fmt = '%#.3f') 
test_digits <- df_defaults %>%
  filter(year == 2070, region == "Midwest", model == "CanESM2") %>%
  filter(sector == "Extreme Temperature", variant == "No Adaptation") %>% 
  filter(impactYear == "2090", impactType == "Cold") %>% 
  select(annual_impacts) %>% as.vector; test_digits

# test_digits %>% format(digits = 6)
# test_digits %>% sprintf(fmt = '%#.6f') 
# c(NA) %>% sprintf(fmt = '%#.6f') 
### -239115535.389834
```


Use the following code to save the results:

* Name the output path and create it if it doesn't exist.
* Then save the outputs file.


```{r saveOutputsPath}
saveOutputsPath <- frediPath %>% file.path("..", "analysis", "qc", today)
if(!dir.exists(saveOutputsPath)){saveOutputsPath %>% dir.create}
df_defaults %>% write.csv(file = file.path(saveOutputsPath, paste0(today, "_qc_outputs.csv")), row.names=F, na="")
```






Create plots



```{r plot types, fig.height=10, fig.width=16}
### Create only heatmaps
# frediPath %>% paste("R", sep="/") %>% load_all()
# defPlots <- df_defaults %>% get_plots(plotTypes="heatmaps")
defPlots <- df_defaults %>% get_plots(plotTypes="heatmaps")
defPlots$heatmaps$SLR
```


Test SV tool 

```{r test sv}
# test_sv <- FrEDI::run_fredi_sv(sector="Coastal Properties")
test_sv <- FrEDI::run_fredi_sv(sector="Coastal Properties", save = T, outpath = saveOutputsPath, addDate = T)
test_sv <- FrEDI::run_fredi_sv(sector="Roads", save = T, outpath = saveOutputsPath, addDate = T)
test_sv <- FrEDI::run_fredi_sv(sector="Labor", save = T, outpath = saveOutputsPath, addDate = T)
test_sv <- FrEDI::run_fredi_sv(sector="Air Quality", save = T, outpath = saveOutputsPath, addDate = T)
test_sv <- FrEDI::run_fredi_sv(sector="High Tide Flooding and Traffic", save = T, outpath = saveOutputsPath, addDate = T)
test_sv <- FrEDI::run_fredi_sv(sector="Extreme Temperature", save = T, outpath = saveOutputsPath, addDate = T)
```


```{r}
test_sv$aveRate_sv %>% is.na %>% which %>% length
```



## Update R Tool [#updateRtool]
### Update Default Outputs

Use the following section to update R defaults

```{r defaultResults}
# ###### Update and Save Default Scenario ######
frediPath %>% load_all
defaultResults <- run_fredi()
# defaultResults <- FrEDI::run_fredi()
save(defaultResults, file=frediPath %>% file.path("data", "defaultResults.rda"))
```



### Update Documentation

Use the following code to update documentation
<!-- usethis::use_data() -->

```{r datasets to include}
# usethis::use_data_raw()
```


```{r updateDocs}
###### Update Documentation ######
###### - Build Manual
###### - Add and build vignettes
###### - Generate Documentation
roxygen2::roxygenise(frediPath)
devtools::document(pkg = frediPath)
# devtools::build_manual(pkg = frediPath)
# devtools::build_vignettes(pkg = frediPath)
```



### Build the Package

Use the following code to build the package

```{r bldPackage}
###### Build Package ######
###### - Build Package but don't include vignettes
devtools::build(pkg=frediPath)
```


### Copy Package Build to Library

```{r package paths}
### Copy the file
packageName      <- "FrEDI"
packageVersion   <- "3.3.0"
packageFile_name <- packageName %>% paste0("_", packageVersion, ".tar.gz")
packageFile_path <- frediPath %>% file.path("..", packageFile_name)
packageDest      <- .libPaths()[1]
packageDest_path <- packageDest %>% file.path(packageFile_name)
### Copy file
file.copy(from = packageFile_path, to = packageDest, overwrite = T)
```

<!-- Copy file -->

<!-- ```{r copy package} -->
<!-- file.copy(from = packageFile_path, to = packageDest, overwrite = T) -->
<!-- ``` -->

<!-- Examine impacts data -->

<!-- ```{r} -->
<!-- testx <- getwd() %>% file.path("inst", "extdata",  "sv", "impacts", "Coastal Flooding and SLR - With Adaptation.csv") %>% read.csv -->
<!-- testx %>% glimpse -->
<!-- testx$block_group %>% unique %>% length -->
<!-- ``` -->





