---
title: "Configure R Tool Data"
author: "Industrial Economics, Inc."
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  rmarkdown::html_document:
    theme: spacelab
    toc: true
    toc_float: true
---

<style>
/* Simplified version of Bootstrap's responsive table CSS */
.table-responsive {
    display: block;
    width: 100%;
    overflow-x: auto;
}

.table-responsive > table {
    width: 100%;
}
</style>


```{r knitr setup, include=FALSE}
### The following parameters declare the options for compiling the Markdown document.
knitr::opts_chunk$set(
  include = T,     ### Evaluate and depict outputs of code chunks in the compiled document
  echo    = T,     ### Echo the commands of the code chunks in the compiled document
  message = FALSE, ### Don't include command-line messages output from evaluating code chunks
  cache   = FALSE, ### Don't cache the evaluation of code chunks
  warning = FALSE,  ### Don't include warnings from evaluating code chunks
  table.format = "html" 
)
```

## Overview

The purpose of this package is to configure the R tool

Load packages 

```{r loadPackages}
### Packages
require(tidyverse)
require(openxlsx)
require(devtools)
# require(ciraTempBin)
# require(kable)
# require(kableExtra)
```


Date of most recent version of the Excel configuration file:

```{r mostRecentDate}
mostRecentDate <- "20210923"
```



```{r declare paths}
### Set system paths
projectPath <- getwd()
today            <- format(Sys.Date(), "%Y%m%d")
### Project configuration
configPath       <- projectPath %>% paste("config", sep="/")
configFiles      <- configPath %>% list.files(".R")
### Code path
codePath         <- projectPath %>% paste("R", sep="/")
codeNames        <- codePath %>% list.files(".R")
configLogPath    <- codePath %>% paste("configLog", sep="/")

### Names for archive and use versions
configFileName   <- "tempBin_config"
configArchName   <- configLogPath %>% paste(configFileName, sep="/") %>% paste(today, sep="_") %>% paste0(".rda")
configUseName    <- codePath %>% paste(configFileName, sep="/") %>% paste0(".rda")

### Output path
dataOutPath      <- projectPath %>% paste("data", sep="/")
dataOutLog       <- dataOutPath %>% paste("dataLog", sep="/")
sysFileName      <- "sysdata"
sysArchName      <- dataOutLog %>% paste(sysFileName, sep="/") %>% paste(today, sep="_") %>% paste0(".rda")
excelFileName    <- mostRecentDate %>% paste("ciraTempBinData.xlsx", sep="_")
sysUseName       <- dataOutPath %>% paste(sysFileName, sep="/") %>% paste0(".rda")

### Path to CIRA project
projectParentDir <- projectPath %>% paste("..", sep="/")
projectParentDir %>% list.files
ciraPath         <- find.package("ciraTempBin", lib.loc=projectParentDir)
```

### Configuration Files

Load all configuration functions

```{r load config}
### Load all functions
configFiles; for(i in configFiles){ source(paste(configPath, i, sep="/")) }
```


List configuration files

```{r}
configLogPath %>% list.files("rda")
```

Update archive:

```{r}
tempBinConfig(outPath = configArchName)
```

Confirm copy was saved:

```{r}
configLogPath %>% list.files("rda")
```

<!-- If a copy was saved, overwrite the config file: -->

<!-- ```{r tempBinConfig} -->
<!-- # tempBinConfig(outPath = configUseName) -->
<!-- ``` -->

### Create Tool Configuration Data


Load configuration data

```{r load configuration file}
# load(configUseName)
```



Load all R functions and configuration files

```{r load config}
### Load all functions
codeNames; for(i in codeNames){ source(paste(codePath, i, sep="/")) }
```

Test system data

```{r}
### Uncomment following two lines to create and save data and check the outputs
time1           <- Sys.time()
test_systemData <- createSystemData(save=F, excelName = excelFileName, silent=T)
time2           <- Sys.time()
time_create     <- time2 - time1; time_create
```


```{r}
(test_systemData$slrImpacts %>% filter(sector=="HTF"))$adaptation %>% unique
# test_systemData$slrImpacts %>% names
# test_systemData$df_results0$sector_label %>% unique
```



If above works, overwrite previous config

```{r save and overwrite data}
### Uncomment following two lines to create and save data and check the outputs
time1           <- Sys.time()
test_systemData <- createSystemData(save=T, excelName = excelFileName, outPath = sysArchName)
test_systemData <- createSystemData(save=T, excelName = excelFileName, silent=T)
time2           <- Sys.time()
time_create     <- time2 - time1; time_create
```





## Update R Tool

Manually update the sysdata.rda file in the Rtool.

After copying and pasting the system data to the Rtool, try detaching ciraTempBin and then loading the package functions. 


Try the package: 167,184 rows

```{r df_defaults, message=T}
ciraPath %>% paste("R", sep="/") %>% load_all
# df_defaults <- tempBin()
# df_defaults <- tempBin(aggLevels = "all")
df_defaults <- tempBin(aggLevels = "all")
df_defaults %>% glimpse
# df_defaults2 <- df_defaults %>% aggregate_impacts(aggLevels="all")
# df_defaults$sector %>% unique
# df_defaults %>% dim
```


```{r}
ciraPath %>% paste("R", sep="/") %>% load_all
df_defaults2 <- df_defaults %>% aggregate_impacts(aggLevels="all")
# df_defaults$sector %>% unique
# df_defaults %>% dim
```



Create plots



```{r plot types, fig.height=10, fig.width=16}
### Create only heatmaps
# ciraPath %>% paste("R", sep="/") %>% load_all()
# defPlots <- df_defaults %>% get_plots(plotTypes="heatmaps")
defPlots <- df_defaults2 %>% get_plots(plotTypes="heatmaps")
defPlots$heatmaps$SLR
```

