---
title: "Example #2"
date: "July, 2023"
description: >
  Running & Analyzing results from FrEDI SV.
#output: rmarkdown::html_vignette
output: html_document
vignette: >
  %\VignetteIndexEntry{Example #2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Running FrEDI's Social Vulnerability Module

This vignette provides a simple example of how to run and analyze data from FrEDI's SV module, under a default scenario, for a specific sector.

**This example script:**

1. [Installs](#installFrEDI) the `FrEDI` R package from GitHub
2. [Sets](#setFrEDI) `FrEDI_SV` input and run parameters.
3. [Runs](#runFrEDI) `FrEDI_SV` with inputs specified in Step 2
4. [Shows](#analyzeFrEDI) example types of analyses using `FrEDI_SV` output data. 

For more information about `FrEDI` or `FrEDI_SV`, see the [About](About.html) page and [FrEDI Technical Documentation](https://www.epa.gov/cira/fredi)

<br>

# Step 1. Install `FrEDI` R package {#installFrEDI}

When installing for the first time, see [Installing & Running FrEDI](manual.html) page.

Load package
```{r load_FrEDI, message = FALSE,results = 'hide'}
library(FrEDI)
```


After successfully [installing `FrEDI`](manual.html), documentation for `FrEDI` functions can be accessed in the same way as for other `R` packages. 

For an overview of `FrEDI`'s user-defined functions, type `library(help="FrEDI")` into an `R` console (this command will show documentation for `FrEDI` even if the package is not installed).

For documentation for a specific function, type `help("*functionName*", package="FrEDI")` into an `R` console, where *functionName* is the name of one of the functions in `FrEDI` (e.g., `help("aggregate_impacts", package="FrEDI")`). 

If `FrEDI` has been installed, users can also search for function-specific documentation in RStudio through the [**Help** window](https://www.r-project.org/help.html). Move the focus to the **Help** window using the keyboard shortcut `Ctrl+3` or toggle the search field in **Help** using `Ctrl+Alt+F1`. Documentation for each function includes examples. 

<br>

# Step 2. Set `FrEDI_SV` Runtime parameters {#setFrEDI}

First, use this chunk to specify & format input projections. Either provide paths to specific files, or set to `NULL` to use default projections for each variable

Use this chunk to specify the input trajectories (temperature, population, GDP) and runtime parameters for `FrEDI_SV`.

```{r setup_fredi_input, results = 'hold', message=FALSE }
# To run FrEDI_SV for more than one scenario, the code below can be
# adapted into a loop to format the inputs for each scenario. 

#***********************************************
#1. Specify & Format Input Trajectories (temperature, population, U.S. GDP)

## Input Files
tempInputFile <- NULL
  # Description: csv file with time series of temperature relative to 1986-2005 average 
  # (units: degC, values: >=0)
  # data must start in 2000 or earlier and can be global or CONUS
  # If global --> must convert to CONUS temperature using the import_inputs() helper function
  # column 1 = 'year', column 2 = 'temp_C'


popInputFile <- NULL
  # Description: csv file with time series of annual NCA regional population (values >= 0) 
  # data must start in 2000 or earlier
  # column 1 = 'year', column 2 = region, column 3 = population (long popform)
  #   NCA region names: 'Midwest', 'Northeast', 'Northern.Plains', 'Northwest',
  #   'Southeast', 'Southern.Plains', 'Southwest'
  # If NULL - use default population trajectory (from ICLUS)

## Input Trajectory parameters
popformFlag = 'long'   
  # Description: Use this to specify the format of the regional population data
  # Options: wide/long. 
  # Wide = columns 2-8 correspond to population in each NCA region. 
  # Long = column 2 = NCA region name ('region'), 
  # column 3 = population for that region ('reg_pop'). 
  # NCA region names: 'Midwest', 'Northeast', 'Northern.Plains', 'Northwest',
  #   'Southeast', 'Southern.Plains', 'Southwest'

temptypeflag <- 'global' 
  # Description: Use this to specify whether the input temperature is global or CONUS
  # import_inputs() will convert to global to CONUS temperature
  # Options: global (input is global T), conus (input is CONUS T)

## Use the import_inputs() helper function to format the input trajectories for use in FrEDI
inputs_list <- import_inputs(tempfile = tempInputFile,
                        popfile = popInputFile,
                        temptype = temptypeflag,
                        popform = popformFlag)

# print out how many custom input files were loaded 
# should be = 1 if using custom temperature only
if ( length(inputs_list) ==0 ){
  print('CONFIRM: No user-specific input data loaded')
} else {
  print( paste('CONFIRM: Number of user-specified input files loaded:',
               length(inputs_list)))
}
```

If no input files are specified, `run_fredi_sv()` will use default temperature and U.S. regional population projections. In this case, `run_fredi_sv()` will calculate annual projected sea level rise based on the default temperature change. 

Default population scenarios are based on UN Median Population projection ([United Nations, 2015](https://www.un.org/en/development/desa/publications/world-population-prospects-2015-revision.html)) and EPA’s ICLUSv2 model ([Bierwagen et al., 2010](https://www.pnas.org/doi/abs/10.1073/pnas.1002096107); [EPA 2017](https://cfpub.epa.gov/ncea/risk/recordisplay.cfm?deid=322479)). Default temperature projections are from the GCAM reference scenario. Current default projections of U.S. national population and U.S. temperature in the year 2090 are 438 million, and 3.4°C respectively. 

<br>

Next, set `FrEDI_SV` runtime parameters
```{r set_fredi_sv, include = TRUE, eval = FALSE}

# Calculate the fredi_sv() results for a single impact sector
# NOTE: the fredi_sv() module takes a few minutes to run because
# the damages are calculated at the Census tract level and then 
# aggregated to the regional level

# take formatted temperature vector from the output of the
# import_inputs() helper function
 temp_C <- inputs_list$tempInput 

# take formatted population vector from the output of the
# import_inputs() helper function
 reg_pop <- inputs_list$popInput

# To see all available sectors, run:
# FrEDI::get_sv_sectorInfo()

# Specify a specific sector
sectorFlag = "Air Quality - Premature Mortality"
  # Purpose:
  #   Specify the SV sector to calculate (can only run one sector at once)
  # Options: run FrEDI::get_sv_sectorInfo() to get a list of the 
  #   current sectors
driverFlag <- temp_C
  # Purpose:
  #   Specify the temperature trajectory to use as an input. 
  #   Temperature needs to be in degrees C, *CONUS* temperature, relative
  #   to the 1986-2005 average baseline
  #   NOTE: if temperature is in global degrees, use the 
  #   FrEDI::convertTemps() helper function to convert from global to CONUS
popFlag <- reg_pop
  # Purpose:
  #   Specify the regional population trajectory to use as an input. 
  #   Population needs to be regional, relative
  #   to the 1986-2005 average baseline, in the long popform format
silentFlag = TRUE
  # Purpose:
  #   Specify the level of messaging desired
  # Options: TRUE/FALSE
saveFlag = FALSE
  # Purpose:
  #   Specify whether to save output results to a pre-formatted Excel workbook
  # Options: TRUE/FALSE
outFlag = getwd()
  # Purpose:
  #   Specify a file directory to save the Excel file.
  # Options: TRUE/FALSE
overwriteFlag = T
  # Purpose: 
  #   Specify whether or not to overwrite any existing Excel workbooks
  # Options: TRUE/FALSE
addDateFlag = FALSE
  # Purpose: 
  #   Specify whether to add the date to the name of the output Excel file if
  # Options: TRUE/FALSE
  # 
```

# Step 3. Run `FrEDI_SV` {#runFrEDI}
Run `FrEDI_SV` using the main `run_fredi_sv()` function 

Default parameter options are used for any parameters that are not specified in `run_fredi_sv()`. 

Note: `run_fredi_sv()` takes longer to run than the main module, `run_fredi()`, as SV damage calculations are conducted at finer spatial scales (e.g., U.S. Census tract vs. regional level).

```{r run_fredi_sv, eval = FALSE, echo=TRUE, results = 'hold',message=TRUE}

#Run FrEDI using inputs and parameters set in Step #2

output_df <- run_fredi_sv(sector      = sectorFlag, 
                          driverInput = driverFlag, 
                          popInput    = popFlag,
                          silent      = silentFlag,
                          save        = saveFlag, 
                          outpath     = outFlag,
                          overwrite   = overwriteFlag,
                          addDate     = addDateFlag) 

# Option: write output
## Write Full Dataframe to CSV (or feather)
# write.csv(output_df$results, './output/example_output.csv')

#First five lines of output dataframe
#output_df$results[1:5,]
```

# Step 4. Analyze `FrEDI_SV` {#analyzeFrEDI}

Results from the `FrEDI::run_fredi_sv()` module can be analyzed directly in R or in the accompanying MS excel workbook (if input `save = TRUE`)

**Disclaimer: These results only provide an illustrative example and should *NOT* be used for further analysis.**

*Example analyses coming soon*

Please contact the `FrEDI` developers with additional questions.
