---
title: "Documentation & Applications"
date: "October, 2023"
description: >
  FrEDI publications and previous applications.
output: rmarkdown::html_vignette
#output: github_document
vignette: >
  %\VignetteIndexEntry{Documentation & Applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../../man/figures/",
  out.width = "100%",
  fig.align="center"
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Documentation

<br>

**Publications**
<br>

Hartin C., E.E. McDuffie, K. Novia, M. Sarofim, B. Parthum, J. Martinich, S. Barr, J. Neumann, J. Willwerth, & A. Fawcett. Advancing the estimates of future climate impacts within the United States, 2023, Earth System Dynamics, https://esd.copernicus.org/articles/14/1015/2023/ 

Sarofim, M.C., Martinich, J., Neumann, J.E. et al. A temperature binning approach for multi-sector climate impact analysis. Climatic Change 165, 22 2021, https://doi.org/10.1007/s10584-021-03048-6
<br>
<br>

**Technical Documentation**
<br>

FrEDI Technical Documentation (last updated July 2023): https://www.epa.gov/system/files/documents/2023-08/Technical%20Documentation%20on%20the%20Framework%20for%20Evaluating%20Damages%20and%20Impacts_MainText_2023.07.pdf 

Technical Documentation Appendix (last updated July 2023): https://www.epa.gov/system/files/documents/2023-08/Technical%20Documentation%20on%20the%20Framework%20for%20Evaluating%20Damages%20and%20Impacts_Appendices_2023.07.pdf 

<br>

---

# Example Applications

FrEDI has been used to explore a variety of questions. Below we link to several recent documents that use FrEDI to assess future impacts of climate change within the U.S. 
<br>

**2023**
<br>

Office of Management and Budget, United States Executive Office of the President, White Paper on Budget Exposure to Increased Costs and Lost Revenue Due to Climate Change: A Preliminary Assessment and Proposed Framework for Future Assessments. March 2023, https://www.whitehouse.gov/wp-content/uploads/2023/03/climate_budget_exposure_fy2024.pdf 
<br>


**2022**
<br>

U.S. Environmental Protection Agency, U.S. EPA Supplementary Material for the RIA for the Supplemental Proposed Rulemaking, NSPS and EG for Existing Sources: Oil and Natural Gas Sector Climate Review – EPA External Review Draft of Report on the Social Cost of Greenhouse Gases: Estimates Incorporating Recent Scientific Advances. September 2022, Docket Number: EPA-HQ-OAR-2021-0317-1549 (https://www.regulations.gov/document/EPA-HQ-OAR-2021-0317-1549)
<br>

**2021**
<br>

United States Department of State and the United States Executive Office of the President, The Long-Term Strategy of the United States: Pathways to Net-Zero Greenhouse Gas Emissions by 2050, Washington DC. November 2021. (https://www.whitehouse.gov/wp-content/uploads/2021/10/US-Long-Term-Strategy.pdf)
