---
title: "Example #1"
date: "July, 2023"
description: >
  Running & Analyzing results from FrEDI's default scenario.
#output: rmarkdown::html_vignette
output: html_document
vignette: >
  %\VignetteIndexEntry{Example #1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Running FrEDI with Default Parameters

FrEDI is commonly used to project the annual, climate-driven physical and economic impacts associated with user-defined trajectories of U.S. temperature change (relative to a 1985-2005 baseline), population, and GDP. 

This vignette provides a simple example of how to run and analyze data from FrEDI's default scenario.

**This example script:**

1. [Installs](#installFrEDI) the `FrEDI` R package from GitHub
2. [Sets](#setFrEDI) `FrEDI` input and run parameters.
3. [Runs](#runFrEDI) `FrEDI` with inputs specified in Step 2
4. [Shows](#analyzeFrEDI) example types of analyses using `FrEDI` output data. 

For more information about `FrEDI`, see the [About](About.html) page and [FrEDI Technical Documentation](https://www.epa.gov/cira/fredi)

<br>

# Step 1. Install `FrEDI` R package {#installFrEDI}

When installing for the first time, see [Installing & Running FrEDI](manual.html) page.

Load package
```{r load_FrEDI, message = FALSE,results = 'hide'}
library(FrEDI)
```

After successfully [installing `FrEDI`](manual.html), documentation for `FrEDI` functions can be accessed in the same way as for other `R` packages. 

For an overview of `FrEDI`'s user-defined functions, type `library(help="FrEDI")` into an `R` console (this command will show documentation for `FrEDI` even if the package is not installed).

For documentation for a specific function, type `help("*functionName*", package="FrEDI")` into an `R` console, where *functionName* is the name of one of the functions in `FrEDI` (e.g., `help("aggregate_impacts", package="FrEDI")`). 

If `FrEDI` has been installed, users can also search for function-specific documentation in RStudio through the [**Help** window](https://www.r-project.org/help.html). Move the focus to the **Help** window using the keyboard shortcut `Ctrl+3` or toggle the search field in **Help** using `Ctrl+Alt+F1`. Documentation for each function includes examples. 

<br>

# Step 2. Set `FrEDI` Runtime parameters {#setFrEDI}

First, use this chunk to specify & format input projections. Either provide paths to specific files, or set to `NULL` to use default projections for each variable

Use this chunk to specify the input trajectories (temperature, population, GDP) and runtime parameters for `FrEDI`.

```{r setup_fredi_input, results = 'hold', message=FALSE }
# To run FrEDI for more than one scenario, the code below can be
# adapted into a loop to format the inputs for each scenario. 

#***********************************************
#1. Specify & Format Input Trajectories (temperature, population, U.S. GDP)

## Input Files
tempInputFile <- NULL
  # Description: csv file with time series of temperature relative to 1986-2005 average 
  # (units: degC, values: >=0)
  # data must start in 2000 or earlier and can be global or CONUS
  # If global --> must convert to CONUS temperature using the import_inputs() helper function
  # column 1 = 'year', column 2 = 'temp_C'

slrInputFile <- NULL 
  # Description: csv file with time series of global mean sea level rise relative to 2000
  # (units: cm, values: >= 0 and <= 250)
  # data must start in 2000 or earlier
  # column 1 = 'year', column 2 = 'slr_cm'
  # If NULL - slr is calculated from the input temperature trajectory

gdpInputFile <- NULL
  # Description: csv file with time series of Gross Domestic Product (units: 2015$, values: >= 0) 
  # data must start in 2000 or earlier
  # column 1 = 'year', column 2 = 'gdp_usd' 
  # If NULL - use default GDP trajectory

popInputFile <- NULL
  # Description: csv file with time series of annual NCA regional population (values >= 0) 
  # data must start in 2000 or earlier
  # column 1 = 'year', columns 2:x = depends on data format (popform)
  # If NULL - use default population trajectory (from ICLUS)


## Input Trajectory parameters
popformFlag = 'wide'   
  # Description: Use this to specify the format of the regional population data
  # Options: wide/long. 
  # Wide = columns 2-8 correspond to population in each NCA region. 
  # Long = column 2 = NCA region name ('region'), 
  # column 3 = population for that region ('reg_pop'). 
  # NCA region names: 'Midwest', 'Northeast', 'Northern.Plains', 'Northwest',
  #   'Southeast', 'Southern.Plains', 'Southwest'

temptypeflag <- 'global' 
  # Description: Use this to specify whether the input temperature is global or CONUS
  # import_inputs() will convert to global to CONUS temperature
  # Options: global (input is global T), conus (input is CONUS T)

## Use the import_inputs() helper function to format the input trajectories for use in FrEDI
inputs_list <- import_inputs(tempfile = tempInputFile,
                        slrfile = slrInputFile,
                        popfile = popInputFile,
                        gdpfile = gdpInputFile,
                        temptype = temptypeflag,
                        popform = popformFlag)

# print out how many custom input files were loaded 
# should be = 1 if using custom temperature only
if ( length(inputs_list) ==0 ){
  print('CONFIRM: No user-specific input data loaded')
} else {
  print( paste('CONFIRM: Number of user-specified input files loaded:',
               length(inputs_list)))
}
```

If no input files are specified, `run_fredi()` will use default temperature, U.S. population, and GDP projections. In this case, `run_fredi()` will calculate annual projected sea level rise based on the default temperature change. 

Default population scenarios are based on UN Median Population projection ([United Nations, 2015](https://www.un.org/en/development/desa/publications/world-population-prospects-2015-revision.html)) and EPA’s ICLUSv2 model ([Bierwagen et al., 2010](https://www.pnas.org/doi/abs/10.1073/pnas.1002096107); [EPA 2017](https://cfpub.epa.gov/ncea/risk/recordisplay.cfm?deid=322479)), and GDP from the EPPA version 6 model ([Chen et al., 2015](https://globalchange.mit.edu/publication/16262)). Default temperature projections are from the GCAM reference scenario. Current default projections of U.S. GDP, national population, and U.S. temperature in the year 2090 are 70 trillion (2015USD), 438 million, and 3.4°C respectively. 

<br>

Next, set `FrEDI` runtime parameters

```{r setup_fredi_parameters, echo=TRUE, results = 'hold', message=FALSE }
thru2300Flag = FALSE
  # Purpose: 
  #   Specify whether to run FrEDI through 2100 (default) or extend to 2300
  # Default: FALSE (will run to 2100)

baseYearFlag <- NULL     
  # Purpose: 
  #   Specify base year for calculating present values of annual impacts
  # Default: 2010

SectorListFlag <- NULL  
  # Purpose: 
  #   Specify the vector of sectors to calculate results for
  # Default: report output for all sectors
  # See FrEDI:get_sectorInfo() for list of all sectors

aggLevelFlag <- c('national','modelaverage','impactyear')
  # Purpose: 
  #   Specify the desired level of results aggregation. For example,
  #   to report national total results across all underlying climate-model 
  #   damage functions, set the flag to c('national','modelaverage')
  # Options: at least one from c('national', 'modelaverage', 'impactyear',
  #   'impacttype', 'all'), or "none". 
  # Default: c('national', 'modelaverage', 'impactyear','impacttype')

pvFlag <- NULL 
  # Purpose: 
  #   Calculate the present value of annual monetized impacts
  # Options: TRUE/FALSE.
  # Default: FALSE

rateFlag <- NULL         
  # Purpose: 
  #   If pvFlag = TRUE, specify the annual constant discount rate used 
  #   to calculate present values
  # Default: 0.03

maxYearFlag <- 2090
  # Purpose: 
  #   Specify the last year of the analysis 
  # Default: 2090

elasticityFlag <- 1   
  # Purpose: 
  #   Specify the income elasticity used to adjust the Value of a
  #   Statistical Life (VSL)
  # Options: any numeric value
  # Default: 0.4

silentFlag <- TRUE       
  # Purpose:
  #   Specify the level of messaging to the user
  # Options: TRUE/FALSE. 
  # Default: TRUE

outputListFlag <- TRUE
  # Purpose:
  #   Specify whether to return input arguments in addition to results data frame
  # Options: TRUE/FALSE. 
  # Default: FALSE
```

<br>

# Step 3. Run `FrEDI` {#runFrEDI}
Run `FrEDI` using the main `run_fredi()` function 

Default parameter options are used for any parameters that are not specified in `run_fredi()`. 

```{r run_fredi, echo=TRUE, results = 'hold',message=TRUE}

#Run FrEDI using inputs and parameters set in Step #2

output_df <- run_fredi(inputsList= inputs_list, 
                       thru2300 = thru2300Flag,
                       sectorList = SectorListFlag,
                       aggLevels=aggLevelFlag,
                       pv = pvFlag,
                       baseYear = baseYearFlag,
                       rate = rateFlag,
                       maxYear = maxYearFlag,
                       elasticity = elasticityFlag,
                       silent = silentFlag,
                       outputList = outputListFlag
                       ) 

# Option: write output
## Write Full Dataframe to CSV (or feather)
# write.csv(output_df$results, './output/example_output.csv')

#First five lines of output dataframe
#output_df$results[1:5,]
```

<br>

# Step 4. Analyze `FrEDI` {#analyzeFrEDI}

The following chunks provide three examples options for how to analyze the raw output dataframe from `FrEDI::run_fredi()`

**Disclaimer: These results only provide an illustrative example and should *NOT* be used for further analysis.**

## Example 1
Extract national average of economic damages (in billions of dollars in 2015$) for all `FrEDI` sectors for a specified year

Output of this chunk includes a snapshot of a subset of the resulting dataframe

*Note: Use the `sectorprimary ==1` and `includeaggregate ==1` flags to filter the `FrEDI` dataframe for impacts from only the default impact sectors and variants.

```{r, example1, echo=TRUE, warning=FALSE, message=FALSE}

#specify year
c_years = c(2090)

#filter and aggregate data, assign to aggregate categories
df_filter <- output_df$results %>%
  # filter for primary sectors and variants (included to avoid 
  #  double counting final impacts)
    filter(sectorprimary ==1,
           includeaggregate ==1) %>%
  # use helper function to aggregate across the impact types of 
  #  each sector
    aggregate_impacts(aggLevels = 'impactType') %>%
  # filter for national aggregate results averaged across all GCMs, 
  #  for the specified year
    filter(model %in% c('Average','Interpolation'),
           region == "National Total",
           year %in% c_years) %>%
  # convert to billions of dollars
    mutate(annual_impacts = annual_impacts /1e9) %>% 
  # round results
    mutate(across(annual_impacts, round, 0)) %>%
  # select (and rename) relevant columns
    select('sector','region','year','annual_impacts') %>%
    rename('billions_2015$' = annual_impacts) 
    

#Display first 10 sectors
library('kableExtra')
kable(df_filter[1:10,], 
      caption = 'Example *Subset* of 2090 Annual National Sectoral Climate-Driven Impacts') %>%
  kable_styling(font_size = 12, full_width = F)

```

## Example 2

Extract national average of physical damages for all `FrEDI` sectors that include physical impacts, for a specified year

Output of this chunk includes a snapshot of a subset of the resulting dataframe

*Note: Use the sectorprimary ==1 and includeaggregate ==1 flags to filter the `FrEDI` dataframe for impacts from only the default impact sectors and variants.

```{r, example2, echo=TRUE, warning=FALSE, message=FALSE}

#specify year
c_years = c(2090)

#filter and aggregate data, assign to aggregate categories
df_filter <- output_df$results %>%
  # filter for primary sectors and variants (included to avoid 
  #  double counting final impacts)
    filter(sectorprimary ==1,
           includeaggregate ==1) %>%
  # filter for national aggregate results averaged across all GCMs
  #  and only include sectors that include physical impacts
    filter(model %in% c('Average','Interpolation'),
           region == "National Total",
           year %in% c_years,
           !(is.na(physicalmeasure))) %>%
  # round results
   mutate(across(c('physical_impacts'), round, 0)) %>%
  # select relevant columns to display
  select('sector','region','year','physicalmeasure',
         'impactType','physical_impacts')

#display first 10 rows
kable(df_filter[1:10,], 
      caption = 'Example *Subset* of 2090 Annual National Sectoral Climate-Driven Physical Impacts') %>%
  kable_styling(font_size = 12, full_width = F)

```

## Example 3
Extract regional economic impacts for `FrEDI` sectors for a specified year

Output of this chunk includes a snapshot of a subset of the resulting dataframe

*Note: Use the sectorprimary ==1 and includeaggregate ==1 flags to filter the `FrEDI` dataframe for impacts from only the default impact sectors and variants.

```{r, example3, echo=TRUE, warning=FALSE, message=FALSE}

#specify year
c_years = c(2090)

#filter and aggregate data, assign to aggregate categories
df_filter <- output_df$results %>%
  # filter for primary sectors and variants (included to avoid 
  #  double counting final impacts)
    filter(sectorprimary ==1,
           includeaggregate ==1) %>%
  # use helper function to aggregate across the impact types of 
  #  each sector
    aggregate_impacts(aggLevels = 'impactType') %>%
  # filter for regional results, averaged across all GCMs, 
  #  for the specified year
    filter(model %in% c('Average','Interpolation'),
           !(region == "National Total"),
           year %in% c_years) %>%
  # convert to billions (2015$)
    mutate(annual_impacts = annual_impacts /1e9) %>%
  # round results
    mutate(across(c('annual_impacts'), round, 0)) %>%
  # sum across all sectors for each region
    group_by_at(.vars = c('region','year')) %>%
     summarize_at(c("annual_impacts"), sum, na.rm=T) %>%
    ungroup %>%
  # select (and rename) relevant columns
    select('region','year','annual_impacts')%>%
    rename('billions_2015$' = annual_impacts)


kable(df_filter[1:7,], 
      caption = 'Example 2090 Annual Climate-Driven Damages, by Region') %>%
  kable_styling(font_size = 12, full_width = F)

```



Please contact the `FrEDI` developers with additional questions.
