---
title: "Example #2"
date: "November 2024"
description: >
  Running & Analyzing results from FrEDI SV.
#output: rmarkdown::html_vignette
output: html_document
vignette: >
  %\VignetteIndexEntry{Example #2}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Running FrEDI's Social Vulnerability Module

This vignette provides a simple example of how to run and analyze data from FrEDI's SV module, under a default scenario, for a specific sector.

**This example script:**

1. [Installs](#installFrEDI) the `FrEDI` R package from GitHub
2. [Sets](#setFrEDI) `FrEDI_SV` input and run parameters.
3. [Runs](#runFrEDI) `FrEDI_SV` with inputs specified in Step 2
4. [Shows](#analyzeFrEDI) example types of analyses using `FrEDI_SV` output data. 

For more information about `FrEDI` or `FrEDI_SV`, see the [About](About.html) page and [FrEDI Technical Documentation](https://www.epa.gov/cira/fredi)

<br>

# Step 1. Install `FrEDI` R package {#installFrEDI}

When installing for the first time, see [Installing & Running FrEDI](manual.html) page.

Load package
```{r load_FrEDI, message=FALSE, results="hide"}
require(FrEDI)
```


After successfully [installing `FrEDI`](manual.html), documentation for `FrEDI` functions can be accessed in the same way as for other `R` packages. 

For an overview of `FrEDI`'s user-defined functions, type `library(help="FrEDI")` into an `R` console (this command will show documentation for `FrEDI` even if the package is not installed).

For documentation for a specific function, type `help("*functionName*", package="FrEDI")` into an `R` console, where `*functionName*` is the name of one of the functions in `FrEDI` (e.g., `help("aggregate_impacts", package="FrEDI")`). Alternatively, use the syntax `?FrEDI::*functionName*` (e.g., `?FrEDI::run_fredi_sv()`).

If `FrEDI` has been installed, users can also search for function-specific documentation in RStudio through the [**Help** window](https://www.r-project.org/help.html). Move the focus to the **Help** window using the keyboard shortcut `Ctrl+3` or toggle the search field in **Help** using `Ctrl+Alt+F1`. Documentation for each function includes examples. 

<br>

# Step 2. Set `FrEDI_SV` Runtime parameters {#setFrEDI}

First, use this chunk to specify & format input projections. Either provide paths to specific files, or set to `NULL` to use default projections for each variable

Use this chunk to specify the input trajectories (temperature, population, GDP) and runtime parameters for `FrEDI_SV`.

```{r setup_fredi_input, results='hold', message=FALSE}
### To run FrEDI_SV for more than one scenario, the code below can be
### adapted into a loop to format the inputs for each scenario. 

###***********************************************
### 1. Specify & Format Input Trajectories (temperature, population, U.S. GDP)

### Input Files
### Population input file
### - Purpose: Specify the population trajectory to use as an input.
### - Requires columns year, region, state, postal, and pop
### - Default: if null, uses default population trajectory
popInputFile <- NULL

### * Temperature input file
### - Description: csv file with time series of temperature relative to 1986-2005 average 
### - (units: degC, values: >=0)
### - Data must start in 2000 or earlier and can be global or CONUS
### - If global, must convert to CONUS temperature using the import_inputs() helper function
### - Contains columns year, temp_C, scenario
tempInputFile <- NULL

### * Temperature type flag
### - Description: Use this to specify whether the input temperature is global or CONUS
### - import_inputs() will convert to global to CONUS temperature
### - Options: global (input is global T), conus (input is CONUS T)
### - Default: defaults to "conus"
temptypeflag <- "global" 

### * Module flag
### - Description: Use this to specify for which module to import inputs 
### - Options: fredi/methane/sv 
### - Default: Defaults to "fredi" if NULL
moduleflag   <- "sv" 

### Use the import_inputs() helper function to format the input trajectories for use in FrEDI
inputs_list <- import_inputs(inputsList = list(
    pop  = popInputFile,
    temp = tempInputFile
  ),
  module = moduleflag
)
inputs_list |> glimpse()
```

If no input files are specified, `run_fredi_sv()` will use default temperature and U.S. regional population projections. In this case, `run_fredi_sv()` will calculate annual projected sea level rise based on the default temperature change. 

Default population scenarios are based on UN Median Population projection ([United Nations, 2015](https://www.un.org/en/development/desa/publications/world-population-prospects-2015-revision.html)) and EPA’s ICLUSv2 model ([Bierwagen et al., 2010](https://www.pnas.org/doi/abs/10.1073/pnas.1002096107); [EPA 2017](https://cfpub.epa.gov/ncea/risk/recordisplay.cfm?deid=322479)). Default temperature projections are from the GCAM reference scenario. Current default projections of U.S. national population and U.S. temperature in the year 2090 are 438 million, and 3.4°C respectively. 

<br>

Next, set `FrEDI_SV` runtime parameters

```{r set_fredi_sv, include=TRUE, eval=FALSE, echo=TRUE, results='hold', message=TRUE}
### Calculate the run_fredi_sv() results for a single impact sector

### NOTE: the run_fredi_sv() module takes a few minutes to run because
### the damages are calculated at the Census tract level and then 
### aggregated to the regional level

### To see all available sectors, run: FrEDI::get_sv_sectorInfo()

### Sector Flag: Specify a specific sector
### - Purpose: Specify the SV sector to calculate (can only run one sector at once)
### - Options: Run FrEDI::get_sv_sectorInfo() to get a list of the possible sectors
sectorFlag  <- "Air Quality - Premature Mortality"
  
### Silent Flag
### - Purpose: Specify the level of messaging desired
### - Options: TRUE/FALSE
silentFlag <- TRUE
```

# Step 3. Run `FrEDI_SV` {#runFrEDI}
Run `FrEDI_SV` using the main `run_fredi_sv()` function 

Default parameter options are used for any parameters that are not specified in `run_fredi_sv()`. 

Note: `run_fredi_sv()` takes longer to run than the main module, `run_fredi()`, as SV damage calculations are conducted at finer spatial scales (e.g., U.S. Census tract vs. regional level).

```{r run_fredi_sv, eval=FALSE, echo=TRUE, results='hold', message=TRUE}
### Run FrEDI using inputs and parameters set in Step 2
output_sv <- run_fredi_sv(
  sector      = sectorFlag, 
  inputsList  = inputs_list,
  silent      = silentFlag
) 

### Glimpse results
output_sv |> glimpse()

### Option: write output
### Write Full Dataframe to CSV (or feather)
# write.csv(output_sv, './output/example_output.csv')

### First five lines of output dataframe
# output_sv[1:5,]
```

# Step 4. Analyze `FrEDI_SV` {#analyzeFrEDI}

Results from the `FrEDI::run_fredi_sv()` module can be analyzed directly in R

**Disclaimer: These results only provide an illustrative example and should *NOT* be used for further analysis.**

*Example analyses coming soon*

Please contact the `FrEDI` developers with additional questions.
