---
title: "Example #1"
description: >
  Running & Analyzing results from FrEDI's default scenario.
#output: rmarkdown::html_vignette
output: html_document
vignette: >
  %\VignetteIndexEntry{Example #1}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(kableExtra)
require(FrEDI)
```



# Running FrEDI with Default Parameters

FrEDI is commonly used to project the annual, temperature and sea level change-driven physical and economic impacts associated with user-defined trajectories of U.S. temperature change (relative to a 1985-2005 baseline), population, and GDP. 

This vignette provides a simple example of how to run and analyze data from FrEDI's default scenario.

**This example script:**

1. [Installs](#installFrEDI) the `FrEDI` R package from GitHub
2. [Sets](#setFrEDI) `FrEDI` input and run parameters
3. [Runs](#runFrEDI) `FrEDI` with inputs specified in Step 2
4. [Shows](#analyzeFrEDI) example types of analyses using `FrEDI` output data

For more information about `FrEDI`, see the [About](About.html) page and [FrEDI Technical Documentation](https://www.epa.gov/cira/fredi)

<br>

# Step 1. Install `FrEDI` R package {#installFrEDI}

When installing for the first time, see the [Installing & Running FrEDI](manual.html) page.

Load package:

```{r load_FrEDI, message=FALSE, results='hide'}
require(FrEDI)
```

After successfully [installing `FrEDI`](manual.html), documentation for `FrEDI` functions can be accessed in the same way as for other `R` packages. 

For an overview of `FrEDI`'s user-defined functions, type `library(help="FrEDI")` into an `R` console (this command will show documentation for `FrEDI` even if the package is not installed).

For documentation for a specific function, type `help("*functionName*", package="FrEDI")` into an `R` console, where `*functionName*` is the name of one of the functions in `FrEDI` (e.g., `help("aggregate_impacts", package="FrEDI")`). Alternatively, use the syntax `?FrEDI::*functionName*` (e.g., `?FrEDI::run_fredi()`).

If `FrEDI` has been installed, users can also search for function-specific documentation in RStudio through the [**Help** window](https://www.r-project.org/help.html). Move the focus to the **Help** window using the keyboard shortcut `Ctrl+3` or toggle the search field in **Help** using `Ctrl+Alt+F1`. Documentation for each function includes examples. 

<br>

# Step 2. Set `FrEDI` Runtime parameters {#setFrEDI}

First, use this chunk to specify & format input projections. Either provide paths to specific files, or set to `NULL` to use default projections for each variable.

Use this chunk to specify the input trajectories (temperature, sea level, population, and/or GDP) and runtime parameters for `FrEDI`.

```{r setup_fredi_input, results='hold', message=FALSE}
### To run FrEDI for more than one scenario, the code below can be
### adapted into a loop to format the inputs for each scenario. 

###***********************************************
### 1. Specify & Format Input Trajectories (temperature, population, U.S. GDP)

### Input Files
### * GDP
### - Description: csv file with time series of U.S. Gross Domestic Product (units: 2015$, values: >= 0) 
### - data must start in 2010 or earlier
### - Must have columns "year", "gdp_usd"
### - If NULL - use default GDP trajectory
gdpInputFile <- NULL

### * Population
### - Description: csv file with time series of annual U.S. population (values >= 0) 
### - Data must start in 2010 or earlier
### - Must have columns "year" and "pop"; other columns may be required, depending on the popArea argument flag
### - If NULL - use default population trajectory (from ICLUS)
popInputFile <- NULL

### * Temperature
### - Description: csv file with time series of temperature relative to 1986-2005 average 
### - (units: degC, values: >=0)
### - data must start in 2000 or earlier and can be global or CONUS
### - If global --> must convert to CONUS temperature using the import_inputs() helper function
### - Must have columns "year", "temp_C"
tempInputFile <- NULL

### * SLR
### - Description: csv file with time series of global mean sea level rise relative to 2000
### - (units: cm, values: >= 0 and <= 250)
### - data must start in 2000 or earlier
### - Must have columns "year", "slr_cm"
### - If NULL - slr is calculated from the input temperature trajectory
slrInputFile <- NULL 

### Input Trajectory Parameters
### * Population area flag
### - Description: Use this to specify the geographical scale of the population data
### - Options: "state","regional","national".
### - For more information, see `?import_inputs()` for more information
popAreaflag  <- "state"   

### * Temperature type flag
### - Description: Use this to specify whether the input temperature is global or CONUS
### - import_inputs() will convert to global to CONUS temperature
### - Options: global (input is global T), conus (input is CONUS T)
### - Default: defaults to "conus"
temptypeflag <- "global" 

### Use the import_inputs() helper function to format the input trajectories for use in FrEDI
inputs_list <- import_inputs(inputsList=list(
     temp = tempInputFile,
    slr  = slrInputFile,
    gdp  = gdpInputFile,
    pop  = popInputFile
  ), temptype = temptypeflag, popArea  = popAreaflag
) ### End import_inputs
inputs_list |> glimpse()
```

If no input files are specified, `run_fredi()` will use default temperature, U.S. population, and GDP projections. In this case, `run_fredi()` will calculate annual projected sea level change based on the default temperature change. 

Default population scenarios are based on UN Median Population projection ([United Nations, 2015](https://www.un.org/en/development/desa/publications/world-population-prospects-2015-revision.html)) and EPA’s ICLUSv2 model ([Bierwagen et al., 2010](https://www.pnas.org/doi/abs/10.1073/pnas.1002096107); [EPA 2017](https://cfpub.epa.gov/ncea/risk/recordisplay.cfm?deid=322479)), and GDP from the EPPA version 6 model ([Chen et al., 2015](https://globalchange.mit.edu/publication/16262)). Default temperature projections are from the GCAM reference scenario. Current default projections of U.S. GDP, national population, and U.S. temperature in the year 2090 are 70 trillion (2015USD), 438 million, and 3.4°C respectively. 

<br>

Next, set `FrEDI` runtime parameters

```{r setup_fredi_parameters, echo=TRUE, results = 'hold', message=FALSE }
### Thru2300 Flag
### - Purpose: Specify whether to run FrEDI through 2100 (default) or extend to 2300
### - Default: FALSE (will run to 2100)
thru2300Flag <-  FALSE

### Sector list flag
### - Purpose: Specify the vector of sectors for which to calculate results
### - Default: Report output for all sectors
### - See FrEDI::get_sectorInfo() for list of all sectors
sectorListFlag <- NULL  

### Aggregation level flag
### - Purpose: Specify the desired level of results aggregation. For example,
###   to report national total results across all underlying GCM 
###   damage functions, set the flag to c("national","modelaverage")
### - Options: at least one from c("national", "modelaverage", "impactyear",
###   "impacttype", "all"), or "none". 
### - Default: c("national", "modelaverage", "impactyear","impacttype")
aggLevelFlag <- c("national", "modelaverage", "impactyear")

### Maximum year flag
### - Purpose: Specify the last year of the analysis 
### - Default: 2100
maxYearFlag <- 2100

### Elasticity flag
### - Purpose: Specify the income elasticity used to adjust the Value of a
###   Statistical Life (VSL)
### Options: any numeric value
### Default: 1
elasticityFlag <- 1   

### Output list flag
### - Purpose: Specify whether to return input arguments in addition to results data frame
### - Options: TRUE/FALSE. 
### - Default: FALSE
outputListFlag <- FALSE

### All columns flag
### - Purpose: Specify whether to include physical and economic multipliers (used in testing)
### - Options: TRUE/FALSE. 
### - Default: FALSE
allColsFlag <- TRUE

### Silent flag
### - Purpose: Specify the level of messaging to the user
### - Options: TRUE/FALSE. 
### - Default: TRUE
silentFlag <- TRUE       
```

<br>

# Step 3. Run `FrEDI` {#runFrEDI}

Run `FrEDI` using the main `run_fredi()` function.

Default parameter options are used for any parameters that are not specified in `run_fredi()`. 

```{r run_fredi, echo=TRUE, results="hold", message=TRUE}
### Run FrEDI using inputs and parameters set in Step #2
output_df <- run_fredi(
  inputsList = inputs_list, 
  sectorList = sectorListFlag,
  # sectorList = "Asphalt Roads",
  aggLevels  = aggLevelFlag,
  elasticity = elasticityFlag,
  maxYear    = maxYearFlag,
  thru2300   = thru2300Flag,
  outputList = outputListFlag,
  allCols    = allColsFlag,
  silent     = silentFlag
) ### End run_fredi
# output_df |> glimpse()
output_df |> pull(model) |> unique()
```

```{r filter_fredi, echo=TRUE, results="hold", message=TRUE}
### Filter to specific year
c_years     <-  c(2100)

### Filter to specific values:
### - Filter to primary sectors
### - Filter to average models/SLR scenario interpolations
### - Filter to specified years
df_primary <- output_df |>
  filter(sectorprimary == 1, includeaggregate >= 1) |>
  filter(model %in% c("Average", "Interpolation"))|>
  filter(year %in% c_years)

### Aggregate across impact types for each sector, calculate billions and round values to nearest dollar
### - Convert to billions of dollars
### - Round values to nearest dollar
conn <- FrEDI:::load_frediDB()
df_sumTypes <- df_primary |> 
  aggregate_impacts(
    conn = conn,
    aggLevels = c("impacttype"), 
    columns   = c("annual_impacts"),
  )
dbDisconnect(conn)
### Option: write output
### Write Full Dataframe to CSV (or feather)
# write.csv(output_df, './output/example_output.csv')

### First five lines of output dataframe
# output_df[1:5,]
```


<br>

# Step 4. Analyze `FrEDI` {#analyzeFrEDI}

The following chunks provide three examples options for how to analyze the raw output dataframe from `FrEDI::run_fredi()`.

**Disclaimer: These results only provide an illustrative example and should *NOT* be used for further analysis.**

## Example 1

Extract national average of economic damages (in billions of dollars in 2015$) for all `FrEDI` sectors for a specified year

The output of this chunk includes a snapshot of a subset of the resulting dataframe.

* Note: Use the `sectorprimary == 1` and `includeaggregate >= 1` flags to filter the `FrEDI` dataframe for impacts from only the default impact sectors and variants. For recommendations on aggregating impacts across sectors, see the FrEDI Technical Documentation (Chapter 2) and `FrEDI::run_fredi()` documentation. 

```{r, example1, echo=TRUE, warning=FALSE, message=FALSE}
### Specify groups
groups1     <- c("sector", "region", "year")
sumCol1     <- c("annual_impacts")
select1     <- groups1 |> c(sumCol1)

### Filter to specific values:
### - Filter for national aggregate results averaged across all GCMs
### - Filter to specified years
### - Select specific columns
df_filter1  <- df_sumTypes |> 
  filter(region == "National Total") |>
  select(all_of(select1)) |>
  rename("billions_2015$" = annual_impacts) |>
  mutate(`billions_2015$` = `billions_2015$` / 1e9) |>
  mutate_at(c("billions_2015$"), round, 2)

### Display first 10 sectors
df_filter1[1:10,] |> 
  kable(caption = "Example *Subset* of 2100 Annual National Sectoral Temperature and Sea Level Change-Driven Impacts") |>
  kable_styling(font_size = 12, full_width = F)
```

## Example 2

Extract national average of physical damages for all `FrEDI` sectors that include physical impacts, for a specified year:

* The output of this chunk includes a snapshot of a subset of the resulting dataframe.
* Note: Use the `sectorprimary == 1` and `includeaggregate >= 1` flags to filter the `FrEDI` dataframe for impacts from only the default impact sectors and variants. For recommendations on aggregating impacts across sectors, see the FrEDI Technical Documentation (Chapter 2) and `FrEDI::run_fredi()` documentation. 

```{r, example2, echo=TRUE, warning=FALSE, message=FALSE}
### Specify groups
groups2     <- c("sector", "impactType", "physicalmeasure", "physical_impacts", "region", "year")
sumCol2     <- c("physical_impacts")
select2     <- groups2  |> c(sumCol2)

### Filter to specific values:
### - Filter for national aggregate results averaged across all GCMs
### - Filter to specified years
### - Select specific columns
df_filter2 <- df_primary |>
  filter(region == "National Total") |>
  filter(!(is.na(physicalmeasure))) |>
  mutate_at(c(sumCol2), round, 0) |>
  select(all_of(select2))

### Display first 10 rows
df_filter2[c(1, 6:9, 14),] |> 
  kable(caption = "Example *Subset* of 2100 Annual National Sectoral Temperature and Sea Level Change-Driven Physical Impacts") |>
  kable_styling(font_size = 12, full_width = F)
```

## Example 3
Extract state economic impacts for `FrEDI` sectors for a specified year:

* The output of this chunk includes a snapshot of a subset of the resulting dataframe.
* Note: Use the `sectorprimary == 1` and `includeaggregate >= 1` flags to filter the `FrEDI` dataframe for impacts from only the default impact sectors and variants. For recommendations on aggregating impacts across sectors, see the FrEDI Technical Documentation (Chapter 2) and `FrEDI::run_fredi()` documentation. 

```{r, example3, echo=TRUE, warning=FALSE, message=FALSE}
### Specify groups
groups3     <- c("sector", "state", "year")
joinCols3   <- c("state", "year")
sumCol3     <- c("annual_impacts")
select3     <- groups3  |> c(sumCol3)

### Filter to specific values:
### - Filter for national aggregate results averaged across all GCMs
### - Filter to specified years
### - Select specific columns
df_filter3 <- df_sumTypes |>
  filter(!(region == "National Total")) |>
  group_by_at(c(groups3)) |>
  summarize_at(c(sumCol3), sum, na.rm=T) |> ungroup() |> 
  ###  SEE RECOMMENDATIONS FOR AGGREGATION in FrEDI TECHNICAL DOCUMENTATION ##
  (function(df0){
    df1 <- df0 |> 
      filter(sector == "Suicide") |> 
      select(-c("sector")) |>
      rename(impacts_suicide=annual_impacts)
    df0 <- df0 |> left_join(df1, by=joinCols3)
    df0 <- df0 |> mutate(impacts_suicide = case_when(impacts_suicide |> is.na() ~ 0, .default=impacts_suicide))
    df0 <- df0 |> mutate(annual_impacts = case_when(
      sector == "ATS Temperature-Related Mortality" ~ annual_impacts - impacts_suicide,
      .default = annual_impacts
    ))
    df0 <- df0 |> select(-c("impacts_suicide"))
    return(df0)
  })() |>
  group_by_at(c(joinCols3)) |>
  summarize_at(c(sumCol3), sum, na.rm=T) |> ungroup() |> 
  rename("billions_2015$" = annual_impacts) |>
  mutate(`billions_2015$` = `billions_2015$` / 1e9) |>
  mutate_at(c("billions_2015$"), round, 2); df_filter3 |> glimpse()

### Display first 10 rows
df_filter3[1:10,] |> 
  kable(caption = "Example 2100 Annual Temperature and Sea Level Change-Driven Damages, by State") |>
  kable_styling(font_size = 12, full_width = F)
```



Please contact the `FrEDI` developers with additional questions.
