---
title: "Documentation & Applications"
date: "October, 2023"
description: >
  FrEDI publications and previous applications.
output: rmarkdown::html_vignette
#output: github_document
vignette: >
  %\VignetteIndexEntry{Documentation & Applications}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "../../man/figures/",
  out.width = "100%",
  fig.align="center"
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Documentation

<br>

**Publications**
<br>

Hartin C., E.E. McDuffie, K. Novia, M. Sarofim, B. Parthum, J. Martinich, S. Barr, J. Neumann, J. Willwerth, & A. Fawcett. 2023. <https://esd.copernicus.org/articles/14/1015/2023/>.

Sarofim, M.C., Martinich, J., Neumann, J.E. et al. 2021. <https://doi.org/10.1007/s10584-021-03048-6>.
<br>
<br>

**Technical Documentation**
<br>

FrEDI Technical Documentation and Appendix: <https://www.epa.gov/cira/about-fredi>.

<br>

---

# Example Applications

The Framework for Evaluating Impacts and Damages (FrEDI) has been used to explore impacts resulting from changes to temperatures and/or sea level to the United States under a variety of future trajectories for population, gross domestic product, temperature, and sea level. For example applications of FrEDI, including recent peer-reviewed literature studies, as well as links to several recent documents that have included analyses or U.S. impact results informed by FrEDI output, see: <https://www.epa.gov/cira/fredi-publications-and-applications>.

<br>
